### 2017-11-06 project.tex
initial commit

\documentclass{article}

\usepackage{martin-style}

\begin{document}

  \begin{definition}
    A topology is...
  \end{definition}

  \begin{theorem}
    An arbitrary intersetion of closed sets is closed.
  \end{theorem}

  \begin{proof}
    Because.
  \end{proof}

\end{document}

### 2018-01-11 project.tex
Prop 2.3 attempt
Proposition 2 part 1

@@
 
-  \begin{definition}
-    A topology is...
-  \end{definition}
-
-  \begin{theorem}
-    An arbitrary intersetion of closed sets is closed.
-  \end{theorem}
+  \begin{proposition}
+      Any finite union of closed sets is closed, and any arbitrary intersection of closed sets is closed.
+  \end{proposition}
 
   \begin{proof}
-    Because.
+  	Proposition 1
+  	\newline
+	X $\in$ $\tau$
+	\newline
+	If U $\subseteq$ X $\wedge$ X$\setminus$U $\in \tau$ then X$\setminus\bigcap$U $\in \tau$
+	\newline
+	If U, V $\subseteq$ X $\wedge$ X$\setminus$U $\in \tau$  $\wedge$ X$\setminus$V $\in \tau$ then X$\setminus$U $\cup$ V $\in \tau$
   \end{proof}
 
+	\begin{proposition}
+		A set K in a topological space X is closed if and only if K contains all its limit points.
+	\end{proposition}
+	\begin{proof}
+		Proposition 2 Part 1 - Prove if K contains all its limit points then that implies X$\setminus$K $\in \tau$
+		\newline
+		$\exists$ x, z, $\alpha, \beta, \lambda, \epsilon \in$ X
+		\newline
+		K $\subseteq$ X, B $\subseteq$ X, C $\subseteq$ X
+		\newline
+		x, z $\in$ K, K = $\lbrace$ y $\mid$ x $\leq$ y $\leq$ z $\rbrace$
+		\newline
+		x, $\alpha, \beta \in$ B, B = $\lbrace \left( \alpha, \beta \right) \mid \alpha <$ x $< \beta  \rbrace$
+		\newline
+		z, $\lambda, \epsilon \in$ C, C = $\lbrace \left( \lambda, \epsilon \right) \mid \lambda <$ z $< \epsilon \rbrace$
+		\newline
+		K $\cap$ B = $[$ x, $\beta  )$, x $\neq \beta \therefore$ x is a limit point.
+		\newline
+		K $\cap$ C = $( \lambda$, z $]$, z $\neq \lambda \therefore$ z is a limit point.
+		\newline
+		x, z $\in$ K, K = $\lbrace$ y $\mid$ x $\leq$ y $\leq$ z $\rbrace \therefore$ K is closed $\Rightarrow$ X$\setminus$K $\in \tau$
+		\newline
+	\end{proof}
+	\begin{proof}
+	Proposition 2 Part 2 - Prove if X$\setminus$K $\in \tau$ then that implies that K contains all of its limit points.
+	\end{proof}
 \end{document}

### 2018-01-17 project.tex
Redo Prop1
update on proof proposition 1

--- 2017-11-06 project.tex
@@
 
-  \begin{definition}
-    A topology is...
-  \end{definition}
-
-  \begin{theorem}
-    An arbitrary intersetion of closed sets is closed.
-  \end{theorem}
+  \begin{proposition}
+      Any finite union of closed sets is closed, and any arbitrary intersection of closed sets is closed.
+  \end{proposition}
 
   \begin{proof}
-    Because.
+  	Proposition 1
+  	\newline
+	A, B $\in \tau \Rightarrow$ A $\cap$ B $\in \tau$ $\Rightarrow \overline{A \cap B} \not\in \tau$
+	\newline
+	$\overline{A \cap B} = \overline{A} \cup \overline{B}$
+	\newline
+	$\overline{A} \cup \overline{B} \not\in \tau$
+	\newline \newline
+	Also:
+	\newline
+	X = (a, z) $\in \tau$
+	\newline
+	A = (j, k) $\in$ X
+	\newline
+	$\overline{A}$ = (a, j] $\cup$ [k, z) $\not\in \tau$
+	\newline \newline
+	If $A \subseteq \tau$ then $\bigcup A \in \tau$
+	\newline
+	If $A$ contains at least one limit point $k$, we call this $\overline{A}$ if $\overline{A} \not\in A$, then $\overline{A} \not\in \tau$
+	\newline
+	If $\overline{A} \not\in \tau$, then $\overline{\bigcup A} \not\in \tau$
+	\newline
+	$\overline{\bigcup A} = \bigcap \overline{A} \not\in \tau$
   \end{proof}
 
+	\begin{proposition}
+		A set K in a topological space X is closed if and only if K contains all its limit points.
+	\end{proposition}
+	\begin{proof}
+		Proposition 2 Part 1 - Prove if K contains all its limit points then that implies X$\setminus$K $\in \tau$
+
+	\end{proof}
+	\begin{proof}
+	Proposition 2 Part 2 - Prove if X$\setminus$K $\in \tau$ then that implies that K contains all of its limit points.
+		\newline
+		Suppose $\exists K \in X$ and that $K$ contains all its limit points.
+		\newline
+		$\exists  x$ such that $x \in X \setminus K$.
+It follows that if $x \in X \setminus K$ then $x \not\in K \Rightarrow x \neq $ limit point $\in K$.
+$\therefore \exists \bigcup x'$ limit points $\in K$
+	\end{proof}
 \end{document}

### 2018-01-23 project.tex
updated prop 1 and 2
prop 2 is likely garbage. Stared at it for hours and got no where.

--- 2017-11-06 project.tex
@@
 
-  \begin{definition}
-    A topology is...
-  \end{definition}
-
-  \begin{theorem}
-    An arbitrary intersetion of closed sets is closed.
-  \end{theorem}
+  \begin{proposition}
+      Any finite union of closed sets is closed, and any arbitrary intersection of closed sets is closed.
+  \end{proposition}
 
   \begin{proof}
-    Because.
+  	Proposition 1 - Any finite union of closed sets is closed.
+  	\newline
+  	Let C, D be closed sets.
+  	\newline
+  	Let A, B be compliments of C, D so A, B are open.
+  	\newline
+  	Then, A $\cap$ B is also open.
+  	\newline
+  	Thus, X$\setminus$(A $\cap$ B) is closed.
+  	\newline
+  	X$\setminus$(A $\cap$ B) = X$\setminus$A $\cap$ X$\setminus$B = C $\cup$ D
+  	\newline\newline
+  	Inductive Proof:
+  	\newline
+  	$\mathcal{C}_1$ = C $\cup$ D, $\mathcal{C}_1$ is closed.
+  	\newline
+  	$\mathcal{C}_2$ = $\mathcal{C}_1 \cup$ E, $\mathcal{C}_2$ is closed.
+  	\newline
+  	$\mathcal{C}_n$ = $\mathcal{C}_1 \cup \mathcal{C}_2 \cup ... \cup \mathcal{C}_(n-1)$, $\mathcal{C}_n$ is closed.
+  	\newline
+  	$\mathcal{C}_(n+1)$ = $\mathcal{C}_n \cup$ Z, $\mathcal{C}_(n+1)$ is closed.
+  	\newline\newline
+  	Proposition 1 - Any arbitrary intersection of closed sets is closed.
+  	\newline
+  	Let $\mathcal{C}$ be a collection of closed sets.
+  	\newline
+  	Let $\mathcal{U}$ be the compliment of $\mathcal{C}$, so $\mathcal{U}$ is a collection of open sets.
+  	\newline
+  	Then, $\bigcup \mathcal{U}$ is also open.
+  	\newline
+  	Thus, X$\setminus\bigcup\mathcal{U}$ is closed.
+  	\newline
+  	X$\setminus\bigcup\mathcal{U}$ = $\bigcap\mathcal{C}$
+  	\newline
+  	Therefore, $\bigcap\mathcal{C}$ is closed.
 	\end{proof}
 
+	\begin{proposition}
+		A set K in a topological space X is closed if and only if K contains all its limit points.
+	\end{proposition}
+	\begin{proof}
+	Proposition 2
+	\newline
+	Let K = X, then K is closed because $\emptyset$ is open.
+	\newline
+	Let x $\in$ X$\setminus$K, so x is not a limit point of K.
+	\newline
+	$\exists \ell \in \mathcal{U}_\ell \in \tau$ such that $\forall$ k $\in$ K besides $\ell$, k $\not\in \mathcal{U}_\ell$
+	\newline
+	Therefore, $\mathcal{U}_\ell$ is the compliment of K, so $\mathcal{U}_\ell$ is open.
+	\newline
+	$\mathcal{U}_\ell$ = X$\setminus$K
+	\newline
+	Thus, X$\setminus$K = $\bigcup$ { $\ell \in \mathcal{U}_\ell$ : $\ell \neq$ k } is open. 
+	\end{proof}
 \end{document}

### 2018-01-30 project.tex
notation correction
update
1/30/18 Update

@@
 
+	\begin{proposition}
+	Puzzle 1: Find an infinite collection of open intervals in $\mathbb{R}$ whose intersection is not an open interval.
+	\end{proposition}
+
+	\begin{proof}
+	$X = \bigcap\lbrace (\frac{-1}{n}, \frac{1}{n}) : n \in \mathbb{Z}^+\rbrace$
+	\end{proof}
   \begin{proposition}
@@
   	\newline
-  	X$\setminus$(A $\cap$ B) = X$\setminus$A $\cap$ X$\setminus$B = C $\cup$ D
+  	X$\setminus$(A $\cap$ B) = X$\setminus$A $\cup$ X$\setminus$B = C $\cup$ D
   	\newline\newline
@@
   	\newline
-  	$\mathcal{C}_1$ = C $\cup$ D, $\mathcal{C}_1$ is closed.
+  	Base Case: C $\cup$ D is closed.
   	\newline
-  	$\mathcal{C}_2$ = $\mathcal{C}_1 \cup$ E, $\mathcal{C}_2$ is closed.
+  	Inductive Hypothesis:
   	\newline
-  	$\mathcal{C}_n$ = $\mathcal{C}_1 \cup \mathcal{C}_2 \cup ... \cup \mathcal{C}_(n-1)$, $\mathcal{C}_n$ is closed.
+  	Assume C$_1$ $\cup $ C$_2 \cup ...$ $\cup $ C$_n$ is closed for closed sets C$_i$.
   	\newline
-  	$\mathcal{C}_(n+1)$ = $\mathcal{C}_n \cup$ Z, $\mathcal{C}_(n+1)$ is closed.
+	Then C$_1$ $\cup $ C$_2 \cup ...$ $\cup $ C$_n$ = K, K $\cup$ C$_{n+1}$ is closed.
   	\newline\newline
@@
   	\newline
-  	Let $\mathcal{U}$ be the compliment of $\mathcal{C}$, so $\mathcal{U}$ is a collection of open sets.
+  	Let $\mathcal{U} = \lbrace$X$\setminus$C : C $\in \mathcal{C}\rbrace$, so $\mathcal{U}$ is a collection of open sets.
   	\newline
@@
 
+	\begin{lemma}
+	A set U is open if and only if for every point $x \in$ U, there exists an open set U$_x$ where $x \in $ U$_x \subseteq$ U
+	\end{lemma}
+	\begin{proof} Suppose U is open
+	\newline
+		Then for all x $\in$ U there exists an open subset of U, U$_x$ such that x $\in$ U$_x$
+	\end{proof}
+	\begin{proof} Suppose there is an open set $\lbrace$U$_x$ : x $\in$ U$_x \rbrace \subseteq$ U.
+	\newline
+	We want to show that U is open.
+	\newline
+	If U$_x \subseteq$ U, then for all $x \in$ U$_x$, $x \in$ U
+	\newline
+	U$_x \subseteq$ U is open if U$_x \subseteq \tau$
+	\newline
+	If U$_x \subseteq \tau$, then $\bigcup$U$_x \in \tau$
+	\newline
+	$\bigcup$U$_x$ = U $\in \tau$, so U is open.
+	\end{proof}
 	\begin{proposition}
@@
 	\end{proposition}
+	\begin{proof} Suppose K contains all its limit points.
+	\newline
+	This is what you had already given
+	\newline
+	If K = X, then K is closed because $\emptyset$ is open.
+	\newline
+	Otherwise let x $\in$ X$\setminus$K, so x is not a limit point of K.
+	\newline
+	Then, $\exists$ $x \in$ U$_x \in \tau$ such that U$_x \cap$ K = $\emptyset$.
+	\newline
+	So, $x \in $ U$_x \subseteq$ X$\setminus$K.
+	\newline
+	Thus, $\bigcup \lbrace$U$_x$ : $x \in$ X$\setminus$K$\rbrace \supseteq$ X$\setminus$K and $\bigcup \lbrace$U$_x$ : $x \in$ X$\setminus$K$\rbrace \subseteq$ X$\setminus$K since U$_x \subseteq$ X$\setminus$K.
+	\newline
+	Therefore, $\bigcup \lbrace$U$_x$ : $x \in$ X$\setminus$K$\rbrace$ = X$\setminus$K, so X$\setminus$K is open and K is closed.
+	\end{proof}
+	\begin{proof} Suppose K is closed.
+	\newline
+		Still unsure how to apply the lemma to the double implication...also unsure if I have the lemma correctly in order to even use it in the first place...
+	\end{proof}
+	\begin{proposition}
+	Verify the discrete and indiscrete topologies are topologies
+	\end{proposition}
+	\begin{proof} Prove the discrete topology is an actual topology.
+	\newline\newline
+	The discrete topology on a set X is $\tau$ = $\mathcal{P}($X$)$
+	\newline
+	$\emptyset$, X $\in \mathcal{P}($X$)$, So $\emptyset,$ X $\in \tau$
+	\newline
+	Let U $\in \tau$, or U $\subseteq \mathcal{P}($X$)$, then the $\bigcup$U $\in \mathcal{P}($X$)$ or $\bigcup$U $\in \tau$
+	\newline
+	Let U, V $\in \tau$, then the intersection of U, V is also in $\tau$.
+	\end{proof}
+	\begin{proof} Prove the indiscrete topology is an actual topology.
+	\newline\newline
+	The indiscrete topology on a set X is given as $\tau$ = $\lbrace \emptyset$, X$\rbrace$.
+	\newline
+	Clearly, $\emptyset$, X $\in \tau$.
+	\newline
+	Let $\mathcal{U}$ be a collection of all open sets in X, then the $\bigcup \mathcal{U}$ is also $\in \tau$.
+	\newline
+	Let U, V be open sets in X, then U, V $\in \tau$.
+	\newline
+	Thus the intersection f open sets U, V is also $\in \tau$
+	\end{proof}
+	\begin{proposition}
+	Find a basis for the indiscrete topology on $\mathbb{R}$.
+	\end{proposition}	
 	\begin{proof}
-	Proposition 2
+	Find a basis for the indiscrete topology on $\mathbb{R}$.
+	\newline\newline
+	The indiscrete topology on $\mathbb{R}$ is given as $\tau$ = $\lbrace \emptyset$, $\mathbb{R}\rbrace$
 	\newline
-	Let K = X, then K is closed because $\emptyset$ is open.
+	A basis on $\mathbb{R}$ is a collection $\mathcal{B} \subseteq \mathcal{P}(\mathbb{R})$ s.t. for each $x \in \mathbb{R}$ $\exists$ B $\in \mathcal{B}$ : $x \in \mathcal{B}$.
 	\newline
-	Let x $\in$ X$\setminus$K, so x is not a limit point of K.
+	Let $\mathcal{B}$ = $\mathbb{R}$. Since $\mathcal{B} \subseteq \mathcal{P}(\mathbb{R})$, for each $x \in \mathbb{R}$, there is a subset B $\in \mathcal{B}$ : $x \in \mathcal{B}$.
 	\newline
-	$\exists \ell \in \mathcal{U}_\ell \in \tau$ such that $\forall$ k $\in$ K besides $\ell$, k $\not\in \mathcal{U}_\ell$
+	Thus, $x \in \mathcal{B}$ and B is a basis on $\mathbb{R}$.
 	\newline
-	Therefore, $\mathcal{U}_\ell$ is the compliment of K, so $\mathcal{U}_\ell$ is open.
+	Furthermore, if two sets B$_1$, B$_2$ $\in \mathcal{B}$, then their intersection is also in $\mathcal{B}$. Let $x \in$ B$_1$, B$_2$. Then $x \in$ B$_1 \cap$ B$_2$.
 	\newline
-	$\mathcal{U}_\ell$ = X$\setminus$K
+	B$_1 \cap$ B$_2$ = B$_3$, so B$_3 \in \mathcal{B}$, and $x \in$ B$_3 \subseteq$ B$_1 \cap$ B$_2$.
 	\newline
-	Thus, X$\setminus$K = $\bigcup$ { $\ell \in \mathcal{U}_\ell$ : $\ell \neq$ k } is open. 
+	Thus B$_3$ is also a basis on $\mathbb{R}$.
 	\end{proof}
+
 \end{document}

### 2018-02-06 project.tex
weekly update

--- 2018-01-23 project.tex
@@
 	\begin{proposition}
+	Puzzle 1: Find an infinite collection of open intervals in $\mathbb{R}$ whose intersection is not an open interval.
+	\end{proposition}
+	\begin{proof}
+	$\bigcap\lbrace (\frac{-1}{n}, \frac{1}{n}) : n \in \mathbb{Z}^+\rbrace = \lbrace 0 \rbrace$ which is not an open interval or open.
+	\end{proof}
+
+  \begin{proposition}
       Any finite union of closed sets is closed, and any arbitrary intersection of closed sets is closed.
   \end{proposition}
-
   \begin{proof}
-  	Proposition 1 - Any finite union of closed sets is closed.
+  	Proposition 1 - We proceed by showing that any finite union of closed sets is closed:
   	\newline
@@
   	\newline
-  	X$\setminus$(A $\cap$ B) = X$\setminus$A $\cap$ X$\setminus$B = C $\cup$ D
+  	By Demorgan's Law, X$\setminus$(A $\cap$ B) = X$\setminus$A $\cup$ X$\setminus$B = C $\cup$ D which is closed.
   	\newline\newline
-  	Inductive Proof:
+	Now that we've shown that C $\cup$ D is closed for all C, D; Assume C$_1$ $\cup $ C$_2 \cup ...$ $\cup $ C$_n$ is closed for closed sets C$_i$.
+Then for C$_1$ $\cup$ ...
+$\cup$ C$_n$ $\cup$ C$_{n+1}$, let K = C$_1$ $\cup$ ...
+$\cup$ C$_n$.
+Thus K $\cup$ C$_{n+1}$ = C$_1$ $\cup$ ...
+$\cup$ C$_n$ $\cup$ C$_{n+1}$ is closed.
 	\newline
-  	$\mathcal{C}_1$ = C $\cup$ D, $\mathcal{C}_1$ is closed.
-  	\newline
-  	$\mathcal{C}_2$ = $\mathcal{C}_1 \cup$ E, $\mathcal{C}_2$ is closed.
-  	\newline
-  	$\mathcal{C}_n$ = $\mathcal{C}_1 \cup \mathcal{C}_2 \cup ... \cup \mathcal{C}_(n-1)$, $\mathcal{C}_n$ is closed.
-  	\newline
-  	$\mathcal{C}_(n+1)$ = $\mathcal{C}_n \cup$ Z, $\mathcal{C}_(n+1)$ is closed.
-  	\newline\newline
-  	Proposition 1 - Any arbitrary intersection of closed sets is closed.
+	Now we show that any arbitrary intersection of closed sets is closed.
   	\newline
@@
   	\newline
-  	X$\setminus\bigcup\mathcal{U}$ = $\bigcap\mathcal{C}$
+  	By Demorgan's Law, X$\setminus\bigcup\mathcal{U}$ = $\bigcap\mathcal{C}$
   	\newline
   	Therefore, $\bigcap\mathcal{C}$ is closed.
+	\end{proof}
+
+	\begin{lemma}
+	A set U is open if and only if for every point $x \in$ U, there exists an open set U$_x$ where $x \in $ U$_x \subseteq$ U
+	\end{lemma}
+	\begin{proof} Suppose U is open, then for all x $\in$ U there exists an open U$_x$ = U, such that x $\in$ U$_x \subseteq$ U.
+	\newline
+	To show the converse, for each x $\in$ U there is an open set U$_x$ where x $\in$ U$_x$ $\subseteq$ U.
+To show that U = $\bigcup \lbrace$ U$_x$ : x $\in$ U $\rbrace$, let x $\in$ U, then for each U$_x$, U $\subseteq$ U$_x$.
+Thus U $\subseteq$ $\bigcup \lbrace$ U$_x$ : x $\in$ U $\rbrace$.
+Now let y $\in$ U$_x$ for some x $\in$ U, then U$_x$ $\subseteq$ U.
+Thus U $\supseteq$ $\bigcup \lbrace$ U$_x$ : x $\in$ U $\rbrace$.
+Therefore U = $\bigcup \lbrace$ U$_x$ : x $\in$ U $\rbrace$.
 	\end{proof}
@@
 	\end{proposition}
+	\begin{proof} Suppose K contains all its limit points.
+	If K = X, then K is closed because $\emptyset$ is open.	Otherwise let x $\in$ X$\setminus$K, so x is not a limit point of K.	Then, $\exists$ $x \in$ U$_x \in \tau$ such that U$_x \cap$ K = $\emptyset$.	So, $x \in $ U$_x \subseteq$ X$\setminus$K.	By the lemma, X$\setminus$K is open so K is closed.
+
+	To show the converse is true as well, let x $\in$ X$\setminus$K, which is an open set by the lemma.
+Since $($X$\setminus$K$)\cap$K is the empty set, x is not a limit point of K.
+So, if $\ell$ is any limit point of K, then $\ell \not\in$ X$\setminus$K, so $\ell \in$ K and K contains all of its limit points.
+	\end{proof}
+
+	\begin{proposition}
+	Verify the discrete and indiscrete topologies are topologies
+	\end{proposition}
+	\begin{proof} To prove the discrete topology is an actual topology, first we define that the discrete topology on a set X is $\tau$ = $\mathcal{P}($X$)$.	$\emptyset$, X $\in \mathcal{P}($X$)$, So $\emptyset,$ X $\in \tau$.
+Now, let $\mathcal{U} \subseteq \tau$ = $\mathcal{P}($X$)$, then the $\bigcup$U $\in \mathcal{P}($X$)$.
+Let U, V $\in \tau$ = $\mathcal{P}($X$)$ then the intersection U $\cap$ V $\in \mathcal{P}($X$)$ = $\tau$.
+Now to show that the indiscrete topology is an actual topology, we define that the indiscrete topology on a set X is given as $\tau$ = $\lbrace \emptyset$, X$\rbrace$.
+Clearly, $\emptyset$, X $\in \tau$.
+Let $\mathcal{U}$ be a collection of open sets in X, then $\bigcup \mathcal{U}$ = X, thus $\bigcup \mathcal{U} \in \tau$.
+	\end{proof}
+
+	\begin{definition}
+	Let $\tau$ be a topology on X. Then $\mathcal{B} \subseteq \tau$ is a basis for $\tau$ if:
+	\newline
+	1. For all x $\in$ U $\in \tau$, there exists B $\in$ $\mathcal{B}$ where x $\in$ B $\subseteq$ U $\in \tau$
+	\newline
+	2. For all B$_1$, B$_2 \in \mathcal{B}$ with x $\in ($B$_1 \cap$ B$_2)$, there exists B$_3 \in \mathcal{B}$ with x $\in$ B$_3 \subseteq$ B$_1 \cap$ B$_2$.
+	\end{definition}
+
+	\begin{theorem}
+	If $\mathcal{B}$ is a basis for $\tau$, then $\tau$ = $\lbrace \bigcup \mathcal{B}^{'}$ : $\mathcal{B}^{'} \in \mathcal{B} \rbrace$. (Every open set is a union of basic sets)
+	\end{theorem}
 	\begin{proof}
-	Proposition 2
-	\newline
-	Let K = X, then K is closed because $\emptyset$ is open.
-	\newline
-	Let x $\in$ X$\setminus$K, so x is not a limit point of K.
-	\newline
-	$\exists \ell \in \mathcal{U}_\ell \in \tau$ such that $\forall$ k $\in$ K besides $\ell$, k $\not\in \mathcal{U}_\ell$
-	\newline
-	Therefore, $\mathcal{U}_\ell$ is the compliment of K, so $\mathcal{U}_\ell$ is open.
-	\newline
-	$\mathcal{U}_\ell$ = X$\setminus$K
-	\newline
-	Thus, X$\setminus$K = $\bigcup$ { $\ell \in \mathcal{U}_\ell$ : $\ell \neq$ k } is open. 
+	Let $\mathcal{B} \subseteq \tau$, then for any $\mathcal{B}^{'} \in \mathcal{B}$, $\mathcal{B}^{'} \in \tau$.
+Furthermore the $\bigcup \mathcal{B}^{'}$ = $\mathcal{B}$, then $\bigcup \mathcal{B}^{'} \subseteq \tau$ and $\bigcup \mathcal{B}^{'}$ = $\tau$.
 	\end{proof}
+
+	\begin{theorem}
+	$\lbrace\mathbb{X}\rbrace$ is a basis for $\tau$ = $\lbrace\emptyset$, $\mathbb{X}\rbrace$. (indiscrete)
+	\end{theorem}
+	\begin{proof}
+	$\mathbb{X}$ $\in \lbrace \emptyset$, $\mathbb{X}\rbrace$ = $\tau$.
+First, let U = $\mathbb{X} \in \tau$, and let x $\in$ U $\in \tau$, then for all x $\in$ U, x $\in \mathbb{X}$, and for some X$_n \in \mathbb{X}$, x $\in$ X$_n$.
+Thus, x $\in$ X$_n \subseteq$ U $\in \tau$.
+Now, we let x $\in$ X$_1$, X$_2$.
+Then x $\in ($X$_1 \cap $X$_2)$.
+Let X$_3 \subseteq ($X$_1 \cap $X$_2)$ such that X$_3$ = $($X$_1 \cap$ X$_2)$ then x $\in$ X$_3$.
+Thus, x $\in$ X$_3 \subseteq ($X$_1 \cap $X$_2) \in \mathbb{X}$.
+Then $\lbrace \mathbb{X} \rbrace$ is a basis for $\tau$ = $\lbrace \emptyset$, $\mathbb{X} \rbrace$.
+	\end{proof}
+
+	\begin{theorem}
+	$\lbrace\lbrace$X$\rbrace$ : x $\in$ X$\rbrace$ is a basis for $\tau$ = $\mathcal{P}($X$)$ = $\lbrace$ U : U $\subseteq$ X$\rbrace$. (discrete)
+	\end{theorem}
+	\begin{proof}
+	The $\bigcup \lbrace$ U : U $\subseteq \mathbb{X} \rbrace$ = $\mathbb{X}$, so for all x $\in$ U, x $\in \mathbb{X} \in \tau$.
+So, there exists X $\subseteq \mathbb{X}$ such that x $\in$ X, thus x $\in$ X $\subseteq \mathbb{X} \in \tau$.
+Again, the $\bigcup \lbrace$ U : U $\subseteq \mathbb{X} \rbrace$ = $\mathbb{X}$, so let x $\in$ X$_1$, X$_2 \subseteq \mathbb{X}$ then x $\in \mathbb{X}$, and x $\in ($X$_1 \cap$ X$_2)$ = X$_3$.
+X$_3$ = $($X$_1 \cap$ X$_2) \subseteq \mathbb{X}$, so X$_3 \in \mathbb{X}$ with x $\in$ X$_3 \subseteq ($X$_1 \cap$ X$_2) \subseteq \mathbb{X} \in \tau$.
+	\end{proof}
+
+	\begin{definition}
+	The Euclidean topology on $\mathbb{R}$ is the topology generated by the basis $\lbrace($a, b$)$ : a $<$ b are in $\mathbb{R}\rbrace$.
+	\end{definition}
+
+	\begin{theorem}
+	$\lbrace($a, b$)$ : a $<$ b $\in \mathbb{R}\rbrace$ is a basis.
+	\end{theorem}
+	\begin{proof}
+	\end{proof}
+
+	\begin{theorem}
+	$\lbrace($a, b$)$ : a $<$ b $\in \mathbb{Q}\rbrace$ is a basis for the Euclidean topology.
+	\end{theorem}
+	\begin{proof}
+	\end{proof}
+
 \end{document}

### 2018-02-06 project.tex
better define basis

@@
 	\begin{definition}
-	Let $\tau$ be a topology on X. Then $\mathcal{B} \subseteq \tau$ is a basis for $\tau$ if:
+		A collection of sets \(\mathcal{B}\subseteq\mathcal{P}(X)\) is
+		called a basis if:
+		\begin{enumerate}
+			\item For all \(x\in X\), there exists \(B\in\mathcal{B}\) such that
+			\(x\in B\).
+			\item  For all \(B_1,B_2 \in \mathcal{B}\) with \(x \in B_1 \cap B_2\), there exists \(B_3 \in \mathcal{B}\) with
+			\(x\in B_3 \subseteq B_1 \cap B_2\).
+		\end{enumerate}
+	  The set \(\{\bigcup\mathcal{B}':\mathcal{B}'\subseteq\mathcal{B}\}\)
+		is called the topology generated by \(\mathcal{B}\).
+	\end{definition}
+
+	\begin{theorem}
+		The ``topology generated by \(\mathcal{B}\)'' is actually a topology.
+	\end{theorem}
+
+	\begin{theorem}
+	Let $\tau$ be a topology on X. Then $\mathcal{B} \subseteq \tau$ generates $\tau$ if:
 	\newline
@@
 	2. For all B$_1$, B$_2 \in \mathcal{B}$ with x $\in ($B$_1 \cap$ B$_2)$, there exists B$_3 \in \mathcal{B}$ with x $\in$ B$_3 \subseteq$ B$_1 \cap$ B$_2$.
-	\end{definition}
+\end{theorem}
 

### 2018-02-18 project.tex
update

@@
 	\begin{proposition}
-	Puzzle 1: Find an infinite collection of open intervals in $\mathbb{R}$ whose intersection is not an open interval.
+	Find an infinite collection of open intervals in $\mathbb{R}$ whose intersection is not an open interval.
 	\end{proposition}
 	\begin{proof}
-	$\bigcap\lbrace (\frac{-1}{n}, \frac{1}{n}) : n \in \mathbb{Z}^+\rbrace = \lbrace 0 \rbrace$ which is not an open interval or open.
+	$\bigcap\lbrace (\frac{-1}{n}, \frac{1}{n}) : n \in \mathbb{Z}^+\rbrace = \lbrace 0 \rbrace$ which is not an open interval or even open.
 	\end{proof}
@@
   \begin{proof}
-  	Proposition 1 - We proceed by showing that any finite union of closed sets is closed:
+	We proceed by showing that any finite union of closed sets is closed:
   	\newline
@@
 $\cup$ C$_n$ $\cup$ C$_{n+1}$, let K = C$_1$ $\cup$ ...
-$\cup$ C$_n$.
-Thus K $\cup$ C$_{n+1}$ = C$_1$ $\cup$ ...
+$\cup$ C$_n$.\newline Thus K $\cup$ C$_{n+1}$ = C$_1$ $\cup$ ...
 $\cup$ C$_n$ $\cup$ C$_{n+1}$ is closed.
@@
 	\newline
-	To show the converse, for each x $\in$ U there is an open set U$_x$ where x $\in$ U$_x$ $\subseteq$ U.
-To show that U = $\bigcup \lbrace$ U$_x$ : x $\in$ U $\rbrace$, let x $\in$ U, then for each U$_x$, U $\subseteq$ U$_x$.
-Thus U $\subseteq$ $\bigcup \lbrace$ U$_x$ : x $\in$ U $\rbrace$.
+	To show the converse, suppose that for each x $\in$ U there is an open set U$_x$ where x $\in$ U$_x$ $\subseteq$ U.
+For $x \in U, x \in U_x$ so $x \in \bigcup \lbrace U_x : x \in U \rbrace$.
+Thus $U \subseteq \bigcup \lbrace U_x : x \in U_x \rbrace$.
 Now let y $\in$ U$_x$ for some x $\in$ U, then U$_x$ $\subseteq$ U.
@@
 	\begin{proof} Suppose K contains all its limit points.
-	If K = X, then K is closed because $\emptyset$ is open.	Otherwise let x $\in$ X$\setminus$K, so x is not a limit point of K.	Then, $\exists$ $x \in$ U$_x \in \tau$ such that U$_x \cap$ K = $\emptyset$.	So, $x \in $ U$_x \subseteq$ X$\setminus$K.	By the lemma, X$\setminus$K is open so K is closed.
+	If K = X, then K is closed because $\emptyset$ is open.	Otherwise let x $\in$ X$\setminus$K, so x is not a limit point of K.	Then, $\exists$ $x \in$ U$_x \in \tau$ such that U$_x \cap$ K = $\emptyset$ since $x \not\in K$.	So, $x \in $ U$_x \subseteq$ X$\setminus$K.	By the lemma, X$\setminus$K is open so K is closed.
 
@@
 	\begin{theorem}
-	If $\mathcal{B}$ is a basis for $\tau$, then $\tau$ = $\lbrace \bigcup \mathcal{B}^{'}$ : $\mathcal{B}^{'} \in \mathcal{B} \rbrace$. (Every open set is a union of basic sets)
+	If $\mathcal{B}$ is a basis for $\tau$, then $\tau$ = $\lbrace \bigcup \mathcal{B}^{'}$ : $\mathcal{B}^{'} \subseteq \mathcal{B} \rbrace$. (Every open set is a union of basic sets)
 	\end{theorem}
 	\begin{proof}
-	Let $\mathcal{B} \subseteq \tau$, then for any $\mathcal{B}^{'} \in \mathcal{B}$, $\mathcal{B}^{'} \in \tau$.
-Furthermore the $\bigcup \mathcal{B}^{'}$ = $\mathcal{B}$, then $\bigcup \mathcal{B}^{'} \subseteq \tau$ and $\bigcup \mathcal{B}^{'}$ = $\tau$.
+	Let $\mathcal{B} \subseteq \tau$, then for any $\mathcal{B}^{'} \subseteq \mathcal{B}$, $\mathcal{B}^{'} \in \tau$.
+Thus $\tau = \lbrace \bigcup \mathcal{B}^{'} : \mathcal{B}^{'} \subseteq \mathcal{B} \rbrace$.
 	\end{proof}
@@
 	\begin{proof}
-	$\mathbb{X}$ $\in \lbrace \emptyset$, $\mathbb{X}\rbrace$ = $\tau$.
-First, let U = $\mathbb{X} \in \tau$, and let x $\in$ U $\in \tau$, then for all x $\in$ U, x $\in \mathbb{X}$, and for some X$_n \in \mathbb{X}$, x $\in$ X$_n$.
-Thus, x $\in$ X$_n \subseteq$ U $\in \tau$.
-Now, we let x $\in$ X$_1$, X$_2$.
-Then x $\in ($X$_1 \cap $X$_2)$.
-Let X$_3 \subseteq ($X$_1 \cap $X$_2)$ such that X$_3$ = $($X$_1 \cap$ X$_2)$ then x $\in$ X$_3$.
-Thus, x $\in$ X$_3 \subseteq ($X$_1 \cap $X$_2) \in \mathbb{X}$.
-Then $\lbrace \mathbb{X} \rbrace$ is a basis for $\tau$ = $\lbrace \emptyset$, $\mathbb{X} \rbrace$.
+	Let $\mathcal{B} = \mathbb{X}$ and let $x \in \mathbb{X}$ so $x \in \mathcal{B}$.
+Then there is $B \subseteq \mathcal{B}$ such that $x \in B$.
+Now consider $B_1, B_2 \in \mathcal{B}$.
+$B_1 = \mathbb{X}$ and $B_2 = \mathbb{X}$ Let $x \in B_1 \cap B_2$ and let $B_3 \subseteq B_1 \cap B_2$, then $x \in B_3 = \mathbb{X}$
 	\end{proof}
@@
 	\begin{theorem}
-	$\lbrace\lbrace$X$\rbrace$ : x $\in$ X$\rbrace$ is a basis for $\tau$ = $\mathcal{P}($X$)$ = $\lbrace$ U : U $\subseteq$ X$\rbrace$. (discrete)
+	$\lbrace\lbrace x \rbrace$ : x $\in$ X$\rbrace$ is a basis for $\tau$ = $\mathcal{P}($X$)$ = $\lbrace$ U : U $\subseteq$ X$\rbrace$. (discrete)
 	\end{theorem}
 	\begin{proof}
-	The $\bigcup \lbrace$ U : U $\subseteq \mathbb{X} \rbrace$ = $\mathbb{X}$, so for all x $\in$ U, x $\in \mathbb{X} \in \tau$.
-So, there exists X $\subseteq \mathbb{X}$ such that x $\in$ X, thus x $\in$ X $\subseteq \mathbb{X} \in \tau$.
-Again, the $\bigcup \lbrace$ U : U $\subseteq \mathbb{X} \rbrace$ = $\mathbb{X}$, so let x $\in$ X$_1$, X$_2 \subseteq \mathbb{X}$ then x $\in \mathbb{X}$, and x $\in ($X$_1 \cap$ X$_2)$ = X$_3$.
-X$_3$ = $($X$_1 \cap$ X$_2) \subseteq \mathbb{X}$, so X$_3 \in \mathbb{X}$ with x $\in$ X$_3 \subseteq ($X$_1 \cap$ X$_2) \subseteq \mathbb{X} \in \tau$.
+	Let $x \in U \in \tau = \mathcal{P}(\mathbb{X})$.
+Then for $B = \lbrace x \rbrace \in \mathcal{B}, x \in B \subseteq U$.
+Let $B_1, B_2 \in \mathcal{B}$.
+Then $B_1 = \lbrace x \rbrace$ and $B_2 = \lbrace y \rbrace$.
 	\end{proof}
@@
 	\begin{definition}
-	The Euclidean topology on $\mathbb{R}$ is the topology generated by the basis $\lbrace($a, b$)$ : a $<$ b are in $\mathbb{R}\rbrace$.
+	The Euclidean topology on $\mathbb{R}$ is the topology generated by the basis \newline $\lbrace(a, b) : a < b \in \mathbb{R}\rbrace$.
 	\end{definition}

### 2018-02-28 project.tex
progress update
update
toplogy generated by B is a topology
2/28/18 update

@@
 	\end{theorem}
-
+	\begin{proof}
+	$\tau$ is $\lbrace \bigcup \mathcal{B}' : \mathcal{B}' \subseteq \mathcal{B} \rbrace$.
+So $\lbrace \bigcup \mathcal{B}' : \mathcal{B}' \subseteq \mathcal{B} \rbrace \subseteq \mathcal{P}(X)$.
+$\emptyset, X \in \tau$ because for $\mathcal{B}' = \emptyset, \bigcup \mathcal{B}' = \emptyset$ and for $\mathcal{B}' = X, \bigcup \mathcal{B}' = X$.
+Let $\mathcal{U} \subseteq \tau$ and $\bigcup \mathcal{U} \in \tau$ because for each $U \in \mathcal{U}, U = \bigcup \mathcal{B}_{U}'$ for some $\mathcal{B}_{U}' \subseteq \mathcal{B}$ So, $\bigcup \mathcal{U} = \bigcup \lbrace \bigcup \mathcal{B}_{U}' : U \in \mathcal{U} \rbrace$.
+Let $\mathcal{B}' = \bigcup \lbrace \mathcal{B}_{U}' : U \in \mathcal{U} \rbrace.$ So, $\bigcup \mathcal{U} = \bigcup \mathcal{B}'.$ \newline For $U, V \in \lbrace \bigcup \mathcal{B}' : \mathcal{B}' \subseteq \mathcal{B} \rbrace, U = B_1$ and $V = B_2, B_1, B_2 \in \mathcal{B}$ such that $B_1 = \mathcal{B}$ and $B_2 = \mathcal{B}$.
+Then $U \cap V \in \lbrace \bigcup \mathcal{B}' : \mathcal{B}' \subseteq \mathcal{B} \rbrace \supseteq W$ so there exists $x \in V, U : x \in U \cap V \supseteq W$.
+Therefore $x \in W \subseteq U \cap V \in \tau$.
+	\end{proof}
 	\begin{theorem}
@@
 	\begin{theorem}
-	If $\mathcal{B}$ is a basis for $\tau$, then $\tau$ = $\lbrace \bigcup \mathcal{B}^{'}$ : $\mathcal{B}^{'} \subseteq \mathcal{B} \rbrace$. (Every open set is a union of basic sets)
-	\end{theorem}
-	\begin{proof}
-	Let $\mathcal{B} \subseteq \tau$, then for any $\mathcal{B}^{'} \subseteq \mathcal{B}$, $\mathcal{B}^{'} \in \tau$.
-Thus $\tau = \lbrace \bigcup \mathcal{B}^{'} : \mathcal{B}^{'} \subseteq \mathcal{B} \rbrace$.
-	\end{proof}
-
-	\begin{theorem}
 	$\lbrace\mathbb{X}\rbrace$ is a basis for $\tau$ = $\lbrace\emptyset$, $\mathbb{X}\rbrace$. (indiscrete)
@@
 	\begin{proof}
-	Let $\mathcal{B} = \mathbb{X}$ and let $x \in \mathbb{X}$ so $x \in \mathcal{B}$.
-Then there is $B \subseteq \mathcal{B}$ such that $x \in B$.
+	Let $\mathcal{B} = \lbrace\mathbb{X}\rbrace$ and let $x \in \mathbb{X} = B \in \mathcal{B}$.
 Now consider $B_1, B_2 \in \mathcal{B}$.
-$B_1 = \mathbb{X}$ and $B_2 = \mathbb{X}$ Let $x \in B_1 \cap B_2$ and let $B_3 \subseteq B_1 \cap B_2$, then $x \in B_3 = \mathbb{X}$
+$B_1 = \mathbb{X}$ and $B_2 = \mathbb{X}$ Let $x \in B_1 \cap B_2$, then $x \in B_3 = \mathbb{X} : B_1 \cap B_2 = X$.
 	\end{proof}
@@
 Let $B_1, B_2 \in \mathcal{B}$.
-Then $B_1 = \lbrace x \rbrace$ and $B_2 = \lbrace y \rbrace$.
+Let $y \in B_1 \cap B_2$ so $B_1 = B_2 = \lbrace y \rbrace$.
+Let $B_3 = \lbrace y \rbrace$ so $y \in B_3 = \lbrace y \rbrace \subseteq B_1 \cap B_2 = \lbrace y \rbrace$.
 	\end{proof}
@@
 	\begin{proof}
+	Let $\mathcal{B} = \lbrace (a, b) : a < b \in \mathbb{R} \rbrace$.
+Let $x \in \mathbb{R}$ and let $B = (x-1, x+1)$, then $B \subseteq \mathbb{R}$ and $B \in \mathcal{B}$.
+\newline For $B_1 = (a_1, b_1)$, $B_2 = (a_2, b_2)$, $a_1<b_1$, $a_2<b_2 \in \mathbb{R}$ with $x \in B_1 \cap B_2$, then there is $B_3 = ( max(a_1, a_2), min(b_1, b_2) ) \subseteq B_1 \cap B_2$ such that $a_1,a_2<x<b_1,b_2 \in B_3$.\newline\newline\newline\newline\newline
 	\end{proof}
@@
 	\begin{proof}
+	Let $\mathcal{B} = \lbrace (a, b) : a<b \in \mathbb{Q}\rbrace$.
+Let $x$, $y \in \mathbb{Q}$ and let $B = (x-y, x+y)$, so $B \subseteq \mathbb{Q}$ and $x \in B \in \mathcal{B}$.
+Now, for $B_1, B_2 \in \mathcal{B}, \exists x \in B_1 \cap B_2 : x \in B_1$ and $x \in B_2$.
+$a_1, a_2 < b_1, b_2 \in \mathbb{Q}.$ Let $B_1 = (a_1, b_1)$ and $B_2 = (a_2, b_2)$.
+Now let $B_3 = (max(a_1,a_2), min(b_1,b_2))$ with $a_1,a_2<x<b_1,b_2 \in \mathcal{B}$.
+So, $x \in B_3 \subseteq B_1 \cap B_2$.
 	\end{proof}

### 2018-03-01 project.tex
add covering properties

@@
 
+	\begin{definition}
+	  A subset \(K\) of a topological space \(X\) is said to be \textbf{compact} if for every
+	  open cover \(\mathcal U\) of \(K\) (every collection \(\mathcal U\) of open sets
+	  such that \(\bigcup \mathcal U=K\)) there exists a finite subcollection
+	  \(\mathcal F\subseteq \mathcal U\) that also covers \(K\) (that is,
+	  \(\bigcup\mathcal F=K\)).
+	\end{definition}
+
+	\begin{theorem}
+	  Any finite union of compact subsets is compact.
+	\end{theorem}
+
+	\begin{proposition}
+	  Any finite subset of a topological space is compact.
+	\end{proposition}
+
+	\begin{proposition}
+	  The subset \(\{0\}\cup\{\frac{1}{n}:n\in\mathbb Z^+\}\) of \(\mathbb R\) is compact.
+	\end{proposition}
+
+	\begin{proposition}
+	  Any unbounded subset of \(\mathbb R\) is not compact.
+	\end{proposition}
+
+	\begin{proposition}
+	  Any open interval \((a,b)\subseteq\mathbb R\) is not compact.
+	\end{proposition}
+
+	\begin{definition}
+	  A subset \(K\) of a topological space \(X\) is said to be \textbf{Lindel\"of} if for every
+	  open cover \(\mathcal U\) of \(K\) (every collection \(\mathcal U\) of open sets
+	  such that \(\bigcup \mathcal U=K\)) there exists a countable subcollection
+	  \(\mathcal F\subseteq \mathcal U\) that also covers \(K\) (that is,
+	  \(\bigcup\mathcal F=K\)).
+	\end{definition}
+
+	\begin{definition}
+	  A subset \(K\) of a topological space \(X\) is said to be \textbf{\(\sigma\)-compact} if
+	  there exist compact subspaces \(K_n\) of \(X\) for \(n\in\mathbb N\) such that
+	  \(K=\bigcup_{n\in\mathbb N} K_n\).
+	\end{definition}
+
+	\begin{definition}
+	  A subset \(K\) of a topological space \(X\) is said to be \textbf{hemicompact} if
+	  there exist compact subspaces \(K_n\) of \(X\) for \(n\in\mathbb N\) such that
+	  \(K=\bigcup_{n\in\mathbb N} K_n\), and for every compact subset \(H\subseteq K\),
+	  \(H\subseteq K_n\) for some \(n\in\mathbb N\).
+	\end{definition}
+
 \end{document}

### 2018-03-08 project.tex
weekly update

@@
 
+	\begin{proof}
+	By definition if $K_1$ and $K_2$ are compact then for each $\mathcal{U}_1$ and $\mathcal{U}_2$ of $K_1$ and $K_2$ such that $\bigcup \mathcal{U}_1 = K_1$ and $\bigcup \mathcal{U}_2 = K_2$.
+So, $\bigcup (\mathcal{U}_1 \cup \mathcal{U}_2) = K_1 \cup K_2$.
+Let $K_3 = K_1 \cup K_2$ and $\mathcal{U}_3 = \mathcal{U}_1 \cup \mathcal{U}_2$.
+Then for $K_3$ there exists $\mathcal{U}_3$ such that $\bigcup \mathcal{U}_3 = K_3$.
+\newline Also by definition there must exist $\mathcal{F}_1$ and $\mathcal{F}_2$ such that $\mathcal{F}_1, \mathcal{F}_2 \subseteq \mathcal{U}_1, \mathcal{U}_2$ respectively.
+Then, $\mathcal{F}_1$ and $\mathcal{F}_2 \subseteq \mathcal{U}_1 \cup \mathcal{U}_2$.
+Let $\mathcal{F}_3 = \mathcal{F}_1 \cup \mathcal{F}_2$, then $\mathcal{F}_3 \subseteq \mathcal{U}_3$.
+Now observe that $\bigcup \mathcal{F}_1 = K_1$ and $\bigcup \mathcal{F}_2 = K_2$.
+The $\bigcup (\mathcal{F}_1 \cup \mathcal{F}_2 ) = K_1 \cup K_2$ and $\bigcup \mathcal{F}_3 = K_1 \cup K_2$ so $K_1 \cup K_2$ must be compact.
+	\end{proof}
+
 	\begin{proposition}
@@
 
+	\begin{proof}
+
+	A subset $K$ of space $\mathbb{X}$ is compact if for every open cover $\mathcal{U}$ of $K$ there exists $\mathcal{F} \subseteq \mathcal{U}$ such that $\bigcup \mathcal{F} = K$.\newline Let $K \subseteq \mathbb{X}$, let $\mathcal{U} = \lbrace (a, b) : a < b \in K \rbrace$ then $\bigcup \mathcal{U} = K$.
+Let $\mathcal{F} = \lbrace F : F = U \in \mathcal{U} \rbrace$, then $\bigcup \mathcal{F} = \bigcup \mathcal{U} = K$, so $\bigcup \mathcal{F} = K$.
+
+	\end{proof}
+
 	\begin{proposition}
@@
 	\end{proposition}
+
+	\begin{proof}
+
+	Assume $K$ is compact, then for all $\mathcal{U}$ of $K$, $\bigcup \mathcal{U} = K$.
+Now we find $\mathcal{F} \subseteq \mathcal{U}$ that also covers $K$.
+For $\bigcup \mathcal{U} = K$, then $0, 1 \in \bigcup \mathcal{U}$.
+Let $\mathbb{A} = \bigcap \lbrace (\frac{-1}{n}, \frac{1}{n}) : n \in \mathbb{Z}^+ \rbrace$ and let $\mathbb{C} = \lbrace \frac{1}{n} : n \in \mathbb{Z}^+$.
+So $\mathbb{A} \subseteq \mathcal{U}$ and $\mathbb{C} \subseteq \mathcal{U}$ so $\mathbb{A} \cup \mathbb{C} \subseteq \mathcal{U}$, let $\mathcal{F} = \mathbb{A} \cup \mathbb{C}$, then $\bigcup \mathcal{F} = \bigcup( \lbrace 0 \rbrace \cup \lbrace \frac{1}{n} : n \in \mathbb{Z}^+ \rbrace)$ so $\bigcup \mathcal{F} = K$.
+
+	\end{proof}
 

### 2018-03-08 project.tex
fix compactness definitions

@@
 	  open cover \(\mathcal U\) of \(K\) (every collection \(\mathcal U\) of open sets
-	  such that \(\bigcup \mathcal U=K\)) there exists a finite subcollection
+	  such that \(\bigcup \mathcal U\supseteq K\)) there exists a finite subcollection
 	  \(\mathcal F\subseteq \mathcal U\) that also covers \(K\) (that is,
-	  \(\bigcup\mathcal F=K\)).
+	  \(\bigcup\mathcal F\supseteq K\)).
 	\end{definition}
@@
 	  open cover \(\mathcal U\) of \(K\) (every collection \(\mathcal U\) of open sets
-	  such that \(\bigcup \mathcal U=K\)) there exists a countable subcollection
+	  such that \(\bigcup \mathcal U\supseteq K\)) there exists a countable subcollection
 	  \(\mathcal F\subseteq \mathcal U\) that also covers \(K\) (that is,
-	  \(\bigcup\mathcal F=K\)).
+	  \(\bigcup\mathcal F\supseteq K\)).
 	\end{definition}

### 2018-03-12 project.tex
add definition-chasing theorems
Updating to include enumeration

--- 2018-03-08 project.tex
@@
 	\end{theorem}
-	\begin{proof}
-	Let $\mathcal{B} = \lbrace\mathbb{X}\rbrace$ and let $x \in \mathbb{X} = B \in \mathcal{B}$.
-Now consider $B_1, B_2 \in \mathcal{B}$.
-$B_1 = \mathbb{X}$ and $B_2 = \mathbb{X}$ Let $x \in B_1 \cap B_2$, then $x \in B_3 = \mathbb{X} : B_1 \cap B_2 = X$.
+	\begin{proof}:\newline
+	\begin{enumerate}
+		\item Let $\mathcal{B} = \lbrace\mathbb{X}\rbrace$ and let $x \in \mathbb{X} = B \in \mathcal{B}$.
+		\item Now consider $B_1, B_2 \in \mathcal{B}$. $B_1 = \mathbb{X}$ and $B_2 = \mathbb{X}$ Let $x \in B_1 \cap B_2$, then $x \in B_3 = \mathbb{X} : B_1 \cap B_2 = X$.
+	\end{enumerate}
 	\end{proof}
@@
 	\end{theorem}
-	\begin{proof}
-	Let $x \in U \in \tau = \mathcal{P}(\mathbb{X})$.
-Then for $B = \lbrace x \rbrace \in \mathcal{B}, x \in B \subseteq U$.
-Let $B_1, B_2 \in \mathcal{B}$.
+	\begin{proof}:\newline
+		\begin{enumerate}
+			\item Let $x \in U \in \tau = \mathcal{P}(\mathbb{X})$. Then for $B = \lbrace x \rbrace \in \mathcal{B}, x \in B \subseteq U$.
+			\item Let $B_1, B_2 \in \mathcal{B}$.
 Let $y \in B_1 \cap B_2$ so $B_1 = B_2 = \lbrace y \rbrace$.
 Let $B_3 = \lbrace y \rbrace$ so $y \in B_3 = \lbrace y \rbrace \subseteq B_1 \cap B_2 = \lbrace y \rbrace$.
+		\end{enumerate}
 	\end{proof}
@@
 	\end{theorem}
-	\begin{proof}
-	Let $\mathcal{B} = \lbrace (a, b) : a < b \in \mathbb{R} \rbrace$.
-Let $x \in \mathbb{R}$ and let $B = (x-1, x+1)$, then $B \subseteq \mathbb{R}$ and $B \in \mathcal{B}$.
-\newline For $B_1 = (a_1, b_1)$, $B_2 = (a_2, b_2)$, $a_1<b_1$, $a_2<b_2 \in \mathbb{R}$ with $x \in B_1 \cap B_2$, then there is $B_3 = ( max(a_1, a_2), min(b_1, b_2) ) \subseteq B_1 \cap B_2$ such that $a_1,a_2<x<b_1,b_2 \in B_3$.\newline\newline\newline\newline\newline
+	\begin{proof}:\newline
+		\begin{enumerate}
+			\item Let $\mathcal{B} = \lbrace (a, b) : a < b \in \mathbb{R} \rbrace$. Let $x \in \mathbb{R}$ and let $B = (x-1, x+1)$, then $B \subseteq \mathbb{R}$ and $B \in \mathcal{B}$.	
+			\item For $B_1 = (a_1, b_1)$, $B_2 = (a_2, b_2)$, $a_1<b_1$, $a_2<b_2 \in \mathbb{R}$ with $x \in B_1 \cap B_2$, then there is $B_3 = ( max(a_1, a_2), min(b_1, b_2) ) \subseteq B_1 \cap B_2$ such that $a_1,a_2<x<b_1,b_2 \in B_3$.
+		\end{enumerate}
 	\end{proof}
@@
 	\end{theorem}
-	\begin{proof}
-	Let $\mathcal{B} = \lbrace (a, b) : a<b \in \mathbb{Q}\rbrace$.
-Let $x$, $y \in \mathbb{Q}$ and let $B = (x-y, x+y)$, so $B \subseteq \mathbb{Q}$ and $x \in B \in \mathcal{B}$.
-Now, for $B_1, B_2 \in \mathcal{B}, \exists x \in B_1 \cap B_2 : x \in B_1$ and $x \in B_2$.
+	\begin{proof}:\newline
+		\begin{enumerate}
+		\item Let $\mathcal{B} = \lbrace (a, b) : a<b \in \mathbb{Q}\rbrace$. Let $x$, $y \in \mathbb{Q}$ and let $B = (x-y, x+y)$, so $B \subseteq \mathbb{Q}$ and $x \in B \in \mathcal{B}$.
+		\item Now, for $B_1, B_2 \in \mathcal{B}, \exists x \in B_1 \cap B_2 : x \in B_1$ and $x \in B_2$.
 $a_1, a_2 < b_1, b_2 \in \mathbb{Q}.$ Let $B_1 = (a_1, b_1)$ and $B_2 = (a_2, b_2)$.
-Now let $B_3 = (max(a_1,a_2), min(b_1,b_2))$ with $a_1,a_2<x<b_1,b_2 \in \mathcal{B}$.
+Now let $B_3 = (max(a_1,a_2), min(b_1,b_2))$ with $a_1,a_2<x<b_1,b_2$ so $x \in B_3$.
 So, $x \in B_3 \subseteq B_1 \cap B_2$.
+		\end{enumerate} 
 	\end{proof}

### 2018-03-14 project.tex
March 14th Update
Compactness properties, THM8

@@
 	\end{proof}
+
 	\begin{theorem}
@@
 \end{theorem}
+\begin{proof}:\newline
+	\begin{enumerate}
+		\item For $x \in U \in \tau$, let $B = \lbrace x \rbrace$, so $x \in B \subseteq U \in \tau$.
+		\item $B_1, B_2 \in \mathcal{B}$. Let $B_3 = (B_1 \cap B_2)$, so $B_3 \subseteq (B_1 \cap B_2)$. Since $x \in (B_1 \cap B_2)$, $x \in B_3$. Thus, $x \in B_3 \subseteq (B_1 \cap B_2)$.
+	\end{enumerate}
+\end{proof}
 
@@
 	\begin{theorem}
-	$\lbrace\lbrace x \rbrace$ : x $\in$ X$\rbrace$ is a basis for $\tau$ = $\mathcal{P}($X$)$ = $\lbrace$ U : U $\subseteq$ X$\rbrace$. (discrete)
+	$\lbrace\lbrace x \rbrace$ : x $\in \mathbb{X}\rbrace$ is a basis for $\tau$ = $\mathcal{P}(\mathbb{X})$ = $\lbrace$ U : U $\subseteq \mathbb{X} \rbrace$. (discrete)
 	\end{theorem}
@@
 			\item Let $\mathcal{B} = \lbrace (a, b) : a < b \in \mathbb{R} \rbrace$. Let $x \in \mathbb{R}$ and let $B = (x-1, x+1)$, then $B \subseteq \mathbb{R}$ and $B \in \mathcal{B}$.	
-			\item For $B_1 = (a_1, b_1)$, $B_2 = (a_2, b_2)$, $a_1<b_1$, $a_2<b_2 \in \mathbb{R}$ with $x \in B_1 \cap B_2$, then there is $B_3 = ( max(a_1, a_2), min(b_1, b_2) ) \subseteq B_1 \cap B_2$ such that $a_1,a_2<x<b_1,b_2 \in B_3$.
+			\item For $B_1 = (a_1, b_1)$, $B_2 = (a_2, b_2)$, $a_1<b_1$, $a_2<b_2 \in \mathbb{R}$ with $x \in B_1 \cap B_2$, then there is $B_3 = ( max(a_1, a_2), min(b_1, b_2) ) \subseteq B_1 \cap B_2$ such that $a_1,a_2<x<b_1,b_2$ so $ x \in B_3$.
 		\end{enumerate}
@@
 	\begin{proof}
-	By definition if $K_1$ and $K_2$ are compact then for each $\mathcal{U}_1$ and $\mathcal{U}_2$ of $K_1$ and $K_2$ such that $\bigcup \mathcal{U}_1 = K_1$ and $\bigcup \mathcal{U}_2 = K_2$.
-So, $\bigcup (\mathcal{U}_1 \cup \mathcal{U}_2) = K_1 \cup K_2$.
-Let $K_3 = K_1 \cup K_2$ and $\mathcal{U}_3 = \mathcal{U}_1 \cup \mathcal{U}_2$.
-Then for $K_3$ there exists $\mathcal{U}_3$ such that $\bigcup \mathcal{U}_3 = K_3$.
-\newline Also by definition there must exist $\mathcal{F}_1$ and $\mathcal{F}_2$ such that $\mathcal{F}_1, \mathcal{F}_2 \subseteq \mathcal{U}_1, \mathcal{U}_2$ respectively.
-Then, $\mathcal{F}_1$ and $\mathcal{F}_2 \subseteq \mathcal{U}_1 \cup \mathcal{U}_2$.
-Let $\mathcal{F}_3 = \mathcal{F}_1 \cup \mathcal{F}_2$, then $\mathcal{F}_3 \subseteq \mathcal{U}_3$.
-Now observe that $\bigcup \mathcal{F}_1 = K_1$ and $\bigcup \mathcal{F}_2 = K_2$.
-The $\bigcup (\mathcal{F}_1 \cup \mathcal{F}_2 ) = K_1 \cup K_2$ and $\bigcup \mathcal{F}_3 = K_1 \cup K_2$ so $K_1 \cup K_2$ must be compact.
+		$K_1$ and $K_2$ are compact so $\bigcup \mathcal{U}_1 \supseteq K_1$ and $\mathcal{U}_2 \supseteq K_2$.
+$\bigcup (\mathcal{U}_1 \cup \mathcal{U}_2) \supseteq K_1 \cup K_2$.
+$K_3 = K_1 \cup K_2$.
+Also, for finite $\mathcal{F}_1 \subseteq \mathcal{U}_1$ and $\mathcal{F}_2 \subseteq \mathcal{U}_2, \bigcup \mathcal{F}_1 \supseteq K_1 and \bigcup \mathcal{F}_2 \supseteq K_2$.
+So, $\bigcup (\mathcal{F}_1 \cup \mathcal{F}_2) \supseteq K_1 \cup K_2$.
+Thus, $K_1 \cup K_2$ is compact.
 	\end{proof}
@@
 
-	A subset $K$ of space $\mathbb{X}$ is compact if for every open cover $\mathcal{U}$ of $K$ there exists $\mathcal{F} \subseteq \mathcal{U}$ such that $\bigcup \mathcal{F} = K$.\newline Let $K \subseteq \mathbb{X}$, let $\mathcal{U} = \lbrace (a, b) : a < b \in K \rbrace$ then $\bigcup \mathcal{U} = K$.
-Let $\mathcal{F} = \lbrace F : F = U \in \mathcal{U} \rbrace$, then $\bigcup \mathcal{F} = \bigcup \mathcal{U} = K$, so $\bigcup \mathcal{F} = K$.
-
+	As shown previously, when $K$ is compact there is $\mathcal{U}$ such that $\bigcup \mathcal{U} \supseteq K$.
+Also, there is a finite $\mathcal{F}$ such that $\bigcup \mathcal{F} \supseteq K$.
+For $F \in \mathcal{F}$, we can find an open covering $\mathcal{U}' \subseteq \mathcal{U}$ such that $\mathcal{U}' \supseteq F$.
+Also, we can find a finite $\mathcal{F}' \subseteq \mathcal{U}'$ such that $\bigcup \mathcal{F}' \supseteq F$.
 	\end{proof}
@@
 	\begin{proof}
-
-	Assume $K$ is compact, then for all $\mathcal{U}$ of $K$, $\bigcup \mathcal{U} = K$.
-Now we find $\mathcal{F} \subseteq \mathcal{U}$ that also covers $K$.
-For $\bigcup \mathcal{U} = K$, then $0, 1 \in \bigcup \mathcal{U}$.
-Let $\mathbb{A} = \bigcap \lbrace (\frac{-1}{n}, \frac{1}{n}) : n \in \mathbb{Z}^+ \rbrace$ and let $\mathbb{C} = \lbrace \frac{1}{n} : n \in \mathbb{Z}^+$.
-So $\mathbb{A} \subseteq \mathcal{U}$ and $\mathbb{C} \subseteq \mathcal{U}$ so $\mathbb{A} \cup \mathbb{C} \subseteq \mathcal{U}$, let $\mathcal{F} = \mathbb{A} \cup \mathbb{C}$, then $\bigcup \mathcal{F} = \bigcup( \lbrace 0 \rbrace \cup \lbrace \frac{1}{n} : n \in \mathbb{Z}^+ \rbrace)$ so $\bigcup \mathcal{F} = K$.
-
+		$K = \lbrace 0 \rbrace \cup \lbrace \frac{1}{n} : n \in \mathbb{Z}^+ \rbrace$.
+Let $\mathcal{U} = \lbrace (n, n+1) : -1 < n < 2 \rbrace$.
+Then $\bigcup \mathcal{U} \supseteq K$.
+Now, there are clearly finitely many $F \in \mathcal{F} \subseteq \mathcal{U}$ such that $\bigcup \mathcal{F} \supseteq K$.
 	\end{proof}
@@
 	\end{proposition}
+	\begin{proof}
+		For a subset to be compact it must be bounded by definition.
+An unbounded $K \subseteq \mathbb{R}$ cannot be compact because there is no finite $\mathcal{F}$ such that $\bigcup \mathcal{F} \supseteq K$ because $K$ itself is not bound so it is impossible for $\bigcup \mathcal{F} \supseteq K$.
+Thus $K$ cannot be compact.
+	\end{proof}
 
@@
 	\end{proposition}
+	\begin{proof}
+		By the same argument, an open interval $(a, b)$ is not bounded, and therefore not compact.
+For every open cover $\mathcal{U}$ of $(a, b)$ has infinitely many $\mathcal{F} \subseteq \mathcal{U}$ such that $\bigcup \mathcal{F} \supseteq (a, b)$.
+So there are not finitely many $F \in \mathcal{F}$ and $(a, b)$ is not compact.
+	\end{proof}
 
@@
 
+	\begin{theorem}
+		Every \(\sigma\)-compact subset of a topological space is Lindel\"of.
+	\end{theorem}
+	\begin{proof}
+		$K_{n \in \mathbb{N}}$ are countable since $\mathbb{N}$ is countable. If $K = \bigcup_{n \in \mathbb{N}} K_n$, then $\bigcup_{n \in \mathbb{N}} K_n \supseteq K$.
+	\end{proof}
+
 	\begin{definition}
@@
 
+	\begin{theorem}
+		Every hemicompact subset of a topological space is \(\sigma\)-compact.
+	\end{theorem}
+	\begin{proof}
+		By definition of $\sigma$-compact, we have compact subspaces $K_n$ such that for $\sigma$-compact $K'$, $K' = \bigcup_{n \in \mathbb{N}} K_n$.
+Obviously, for any subset $H$ of the hemicompact set $K$, $H \subseteq K_n \subseteq K$ and since $K' = \bigcup_{n \in \mathbb{N}} K_n, H \subseteq K'$.
+	\end{proof}
+
 \end{document}

### 2018-03-27 project.tex
Update
Numbers 8, 13, 15, 16, 17, 18 editted

@@
 	\end{theorem}
-	\begin{proof}
+	\begin{proof} NEEDS WORK\newline
 	$\tau$ is $\lbrace \bigcup \mathcal{B}' : \mathcal{B}' \subseteq \mathcal{B} \rbrace$.
@@
 	\begin{enumerate}
-		\item For $x \in U \in \tau$, let $B = \lbrace x \rbrace$, so $x \in B \subseteq U \in \tau$.
-		\item $B_1, B_2 \in \mathcal{B}$. Let $B_3 = (B_1 \cap B_2)$, so $B_3 \subseteq (B_1 \cap B_2)$. Since $x \in (B_1 \cap B_2)$, $x \in B_3$. Thus, $x \in B_3 \subseteq (B_1 \cap B_2)$.
+		\item For $x \in \mathbb{X} \in \tau$, select $x \in B \in \mathcal{B}$, so $x \in \mathbb{X}$ and $x \in B$, then $x \in B \subseteq \mathbb{X} \in \tau$.
+		\item See definition 6-2.
+		\item Let $\mathcal{B'} \subseteq \mathcal{B}$ and $\mathcal{B'} = \mathcal{B}$ ,so $\bigcup \mathcal{B'} = \bigcup \mathcal{B} = \tau$.
 	\end{enumerate}
@@
 		\item Let $\mathcal{B} = \lbrace\mathbb{X}\rbrace$ and let $x \in \mathbb{X} = B \in \mathcal{B}$.
-		\item Now consider $B_1, B_2 \in \mathcal{B}$. $B_1 = \mathbb{X}$ and $B_2 = \mathbb{X}$ Let $x \in B_1 \cap B_2$, then $x \in B_3 = \mathbb{X} : B_1 \cap B_2 = X$.
+		\item Now consider $B_1, B_2 \in \mathcal{B}$. $B_1 = \mathbb{X}$ and $B_2 = \mathbb{X}$ Let $x \in B_1 \cap B_2$, then $x \in B_3 = \mathbb{X} : B_1 \cap B_2 = \mathbb{X}$.
 	\end{enumerate}
@@
 			\item Let $x \in U \in \tau = \mathcal{P}(\mathbb{X})$. Then for $B = \lbrace x \rbrace \in \mathcal{B}, x \in B \subseteq U$.
-			\item Let $B_1, B_2 \in \mathcal{B}$.
-Let $y \in B_1 \cap B_2$ so $B_1 = B_2 = \lbrace y \rbrace$.
-Let $B_3 = \lbrace y \rbrace$ so $y \in B_3 = \lbrace y \rbrace \subseteq B_1 \cap B_2 = \lbrace y \rbrace$.
+			\item Let $B_1, B_2 \in \mathcal{B}$. Let $y \in B_1 \cap B_2$. Let $B_3 = \lbrace y \rbrace$ $y \in B_3 = \lbrace y \rbrace \subseteq B_1 \cap B_2$. 
 		\end{enumerate}
@@
 		\begin{enumerate}
-			\item Let $\mathcal{B} = \lbrace (a, b) : a < b \in \mathbb{R} \rbrace$. Let $x \in \mathbb{R}$ and let $B = (x-1, x+1)$, then $B \subseteq \mathbb{R}$ and $B \in \mathcal{B}$.	
+			\item Let $\mathcal{B} = \lbrace (a, b) : a < b \in \mathbb{R} \rbrace$. Let $x \in \mathbb{R}$ and let $B = (x-1, x+1)$, then $x \in B \subseteq \mathbb{R}$ and $B \in \mathcal{B}$.	
 			\item For $B_1 = (a_1, b_1)$, $B_2 = (a_2, b_2)$, $a_1<b_1$, $a_2<b_2 \in \mathbb{R}$ with $x \in B_1 \cap B_2$, then there is $B_3 = ( max(a_1, a_2), min(b_1, b_2) ) \subseteq B_1 \cap B_2$ such that $a_1,a_2<x<b_1,b_2$ so $ x \in B_3$.
@@
 		\begin{enumerate}
-		\item Let $\mathcal{B} = \lbrace (a, b) : a<b \in \mathbb{Q}\rbrace$. Let $x$, $y \in \mathbb{Q}$ and let $B = (x-y, x+y)$, so $B \subseteq \mathbb{Q}$ and $x \in B \in \mathcal{B}$.
+		\item Let $\mathcal{B} = \lbrace (a, b) : a < b \in \mathbb{Q}\rbrace$ Let $x \in \mathbb{R}$ then, $\llcorner x \lrcorner -1 < x < \ulcorner x \urcorner + 1$.
+Let B = $(\llcorner x \lrcorner -1, \ulcorner x \urcorner + 1)$, so $x \in B \in \mathcal{B}$ and $B \subseteq \mathbb{Q}$.
 		\item Now, for $B_1, B_2 \in \mathcal{B}, \exists x \in B_1 \cap B_2 : x \in B_1$ and $x \in B_2$.
@@
 	\begin{proof}
-		$K_1$ and $K_2$ are compact so $\bigcup \mathcal{U}_1 \supseteq K_1$ and $\mathcal{U}_2 \supseteq K_2$.
-$\bigcup (\mathcal{U}_1 \cup \mathcal{U}_2) \supseteq K_1 \cup K_2$.
+	$K_1$ and $K_2$ are compact, so let $\mathcal{U}_1$ and $\mathcal{U}_2$ be open covers of $K_1$ and$K_2$ respectively.
+So $\bigcup \mathcal{U}_1 \supseteq K_1$, and $\bigcup \mathcal{U}_2 \supseteq K_2$ and $\bigcup (\mathcal{U}_1 \cup \mathcal{U}_2) \supseteq K_1 \cup K_2$.
 $K_3 = K_1 \cup K_2$.
-Also, for finite $\mathcal{F}_1 \subseteq \mathcal{U}_1$ and $\mathcal{F}_2 \subseteq \mathcal{U}_2, \bigcup \mathcal{F}_1 \supseteq K_1 and \bigcup \mathcal{F}_2 \supseteq K_2$.
-So, $\bigcup (\mathcal{F}_1 \cup \mathcal{F}_2) \supseteq K_1 \cup K_2$.
-Thus, $K_1 \cup K_2$ is compact.
+There is a $\mathcal{U}_3 \supseteq K_3$.
+So let $\mathcal{U}_1 = \mathcal{U}_3$ and $\mathcal{U}_2 = \mathcal{U}_3$.
+For finite $\mathcal{F}_3 \subseteq \mathcal{U}_3, \mathcal{F}_3 \supseteq K_3$, so $\mathcal{F}_3 \supseteq K_1 \cup K_2$.
+Let $\mathcal{F}_1 = \mathcal{F}_3$ and $\mathcal{F}_2 = \mathcal{F}_3$, so $K_1 \cup K_2$ is compact.
 	\end{proof}
@@
 	\begin{proof}
-
-	As shown previously, when $K$ is compact there is $\mathcal{U}$ such that $\bigcup \mathcal{U} \supseteq K$.
-Also, there is a finite $\mathcal{F}$ such that $\bigcup \mathcal{F} \supseteq K$.
-For $F \in \mathcal{F}$, we can find an open covering $\mathcal{U}' \subseteq \mathcal{U}$ such that $\mathcal{U}' \supseteq F$.
-Also, we can find a finite $\mathcal{F}' \subseteq \mathcal{U}'$ such that $\bigcup \mathcal{F}' \supseteq F$.
+	For $F = \lbrace x_i : 0 \leq x_i < n \rbrace \subseteq \mathbb{X}$, let $\mathcal{U}$ be an open covering on $F$ so $\bigcup \mathcal{U} \supseteq F$.
+Then we can find  a finite $\mathcal{F} \subseteq \mathcal{U}$ such that $\bigcup \mathcal{F} \supseteq F$.
+Suppose $\mathcal{U}_0 = \lbrace x_0 : -1 \leq x_0 < n+1 \rbrace \subseteq \mathcal{U}$ then let $\mathcal{F} = \mathcal{U}_0$, so $\bigcup \mathcal{F} \supseteq F$.
 	\end{proof}
@@
 	\begin{proof}
-		$K = \lbrace 0 \rbrace \cup \lbrace \frac{1}{n} : n \in \mathbb{Z}^+ \rbrace$.
-Let $\mathcal{U} = \lbrace (n, n+1) : -1 < n < 2 \rbrace$.
-Then $\bigcup \mathcal{U} \supseteq K$.
-Now, there are clearly finitely many $F \in \mathcal{F} \subseteq \mathcal{U}$ such that $\bigcup \mathcal{F} \supseteq K$.
+	Let $K = \lbrace 0 \rbrace \cup \lbrace \frac{1}{n} : n \in \mathbb{Z^+} \rbrace \subseteq \mathbb{R}$ and let $\mathcal{U}$ be an open covering on $K$ such that $\bigcup \mathcal{U} \supseteq K$.
+So for $\mathcal{U}_0 \subseteq \mathcal{U}, \mathcal{U}_0 = \lbrace n_0 : -1 \leq n_0 \leq 2, n_0 \in \mathbb{Z} \rbrace$.
+$\bigcup \mathcal{U}_0 \supseteq K$.
+So, let finite $\mathcal{F} = \mathcal{U}_0$, so $\mathcal{F} \subseteq \mathcal{U}$ and $\mathcal{F} \supseteq K$.
 	\end{proof}
@@
 	\begin{proof}
-		For a subset to be compact it must be bounded by definition.
-An unbounded $K \subseteq \mathbb{R}$ cannot be compact because there is no finite $\mathcal{F}$ such that $\bigcup \mathcal{F} \supseteq K$ because $K$ itself is not bound so it is impossible for $\bigcup \mathcal{F} \supseteq K$.
-Thus $K$ cannot be compact.
+	For unbounded $K \subseteq \mathbb{R}$ suppose there is an open covering $\mathcal{U}$ on $K$.
+Then there exists a finite $\mathcal{F} \subseteq \mathcal{U}$ such that $\bigcup \mathcal{F} \supseteq K$.
+For $\mathcal{F}$ to be finite it must be bounded.
+So, there is no $\bigcup \mathcal{F} \supseteq K$.
+Essentially we would need $\mathcal{F} = \lbrace (- \infty , n) : n \in \mathbb{Z^-} \rbrace \cup \lbrace (n-3, \infty) : n \in \mathbb{Z^+} \rbrace$ which is not finite.
 	\end{proof}
@@
 	\begin{proof}
-		By the same argument, an open interval $(a, b)$ is not bounded, and therefore not compact.
-For every open cover $\mathcal{U}$ of $(a, b)$ has infinitely many $\mathcal{F} \subseteq \mathcal{U}$ such that $\bigcup \mathcal{F} \supseteq (a, b)$.
-So there are not finitely many $F \in \mathcal{F}$ and $(a, b)$ is not compact.
 	\end{proof}
@@
 	\begin{proof}
-		$K_{n \in \mathbb{N}}$ are countable since $\mathbb{N}$ is countable. If $K = \bigcup_{n \in \mathbb{N}} K_n$, then $\bigcup_{n \in \mathbb{N}} K_n \supseteq K$.
 	\end{proof}
@@
 	\begin{proof}
-		By definition of $\sigma$-compact, we have compact subspaces $K_n$ such that for $\sigma$-compact $K'$, $K' = \bigcup_{n \in \mathbb{N}} K_n$.
-Obviously, for any subset $H$ of the hemicompact set $K$, $H \subseteq K_n \subseteq K$ and since $K' = \bigcup_{n \in \mathbb{N}} K_n, H \subseteq K'$.
+		This proof is trivial as it is defined as stated here in definition 21.
 	\end{proof}

### 2018-03-29 project.tex
Update
8, 9, 10, 16, 17, 18

@@
 	\begin{enumerate}
-		\item For $x \in \mathbb{X} \in \tau$, select $x \in B \in \mathcal{B}$, so $x \in \mathbb{X}$ and $x \in B$, then $x \in B \subseteq \mathbb{X} \in \tau$.
+		\item For $x \in \mathbb{X} \in \tau$, select $x \in B \subseteq \mathbb{X} \in \tau$, so 1 of definition 6 holds.
 		\item See definition 6-2.
-		\item Let $\mathcal{B'} \subseteq \mathcal{B}$ and $\mathcal{B'} = \mathcal{B}$ ,so $\bigcup \mathcal{B'} = \bigcup \mathcal{B} = \tau$.
+		\item Let $U \in \tau$, then for every $B \subseteq U, B \in \mathcal{B}$.
+Let $\mathcal{B'} = \lbrace B : B \in \mathcal{B} \rbrace$ so $U = \bigcup \mathcal{B'}$.
+Now let $\mathcal{B'} \subseteq \mathcal{B}$ such that for each $B \in \mathcal{B}, B \in \mathcal{B'}$ so $\bigcup \mathcal{B'} = U$.
 		\end{enumerate}
@@
 		\item Now consider $B_1, B_2 \in \mathcal{B}$. $B_1 = \mathbb{X}$ and $B_2 = \mathbb{X}$ Let $x \in B_1 \cap B_2$, then $x \in B_3 = \mathbb{X} : B_1 \cap B_2 = \mathbb{X}$.
+		\item Choose $\mathcal{B}_\emptyset \subseteq \mathcal{B}$ and $\mathcal{B}_\mathbb{X} \subseteq \mathcal{B}$ where $\bigcup \mathcal{B}_\emptyset = \emptyset$ and $\bigcup \mathcal{B}_\mathbb{X} = \mathbb{X}$, so $\bigcup \mathcal{B} = \tau = \lbrace \emptyset, \mathbb{X} \rbrace$.
 	\end{enumerate}
@@
 	\begin{theorem}
-	$\lbrace\lbrace x \rbrace$ : x $\in \mathbb{X}\rbrace$ is a basis for $\tau$ = $\mathcal{P}(\mathbb{X})$ = $\lbrace$ U : U $\subseteq \mathbb{X} \rbrace$. (discrete)
+	$\mathcal{B} = \lbrace\lbrace x \rbrace$ : x $\in \mathbb{X}\rbrace$ is a basis for $\tau$ = $\mathcal{P}(\mathbb{X})$ = $\lbrace$ U : U $\subseteq \mathbb{X} \rbrace$. (discrete)
 	\end{theorem}
@@
 			\item Let $B_1, B_2 \in \mathcal{B}$. Let $y \in B_1 \cap B_2$. Let $B_3 = \lbrace y \rbrace$ $y \in B_3 = \lbrace y \rbrace \subseteq B_1 \cap B_2$. 
+			\item For every $x \in \mathbb{X}$ there are $B_x \in \mathcal{B}$ so $\bigcup \mathcal{B} = \bigcup \lbrace x : x \in \mathbb{X} \rbrace = \tau = \mathcal{P}(\mathbb{X})$.
 		\end{enumerate}
@@
 		\begin{enumerate}
-		\item Let $\mathcal{B} = \lbrace (a, b) : a < b \in \mathbb{Q}\rbrace$ Let $x \in \mathbb{R}$ then, $\llcorner x \lrcorner -1 < x < \ulcorner x \urcorner + 1$.
-Let B = $(\llcorner x \lrcorner -1, \ulcorner x \urcorner + 1)$, so $x \in B \in \mathcal{B}$ and $B \subseteq \mathbb{Q}$.
+		\item Let $\mathcal{B} = \lbrace (a, b) : a < b \in \mathbb{Q}\rbrace$ Let $x \in \mathbb{R}$ then, $\lfloor x \rfloor -1 < x < \lceil x \rceil + 1$.
+Let B = $(\lfloor x \rfloor -1, \lceil x \rceil + 1)$, so $x \in B \in \mathcal{B}$ and $B \subseteq \mathbb{Q}$.
 		\item Now, for $B_1, B_2 \in \mathcal{B}, \exists x \in B_1 \cap B_2 : x \in B_1$ and $x \in B_2$.
@@
 So, $x \in B_3 \subseteq B_1 \cap B_2$.
+		\item Now show it generates $\tau$...
 		\end{enumerate} 
@@
 	\begin{proof}
-	$K_1$ and $K_2$ are compact, so let $\mathcal{U}_1$ and $\mathcal{U}_2$ be open covers of $K_1$ and$K_2$ respectively.
-So $\bigcup \mathcal{U}_1 \supseteq K_1$, and $\bigcup \mathcal{U}_2 \supseteq K_2$ and $\bigcup (\mathcal{U}_1 \cup \mathcal{U}_2) \supseteq K_1 \cup K_2$.
-$K_3 = K_1 \cup K_2$.
-There is a $\mathcal{U}_3 \supseteq K_3$.
-So let $\mathcal{U}_1 = \mathcal{U}_3$ and $\mathcal{U}_2 = \mathcal{U}_3$.
-For finite $\mathcal{F}_3 \subseteq \mathcal{U}_3, \mathcal{F}_3 \supseteq K_3$, so $\mathcal{F}_3 \supseteq K_1 \cup K_2$.
-Let $\mathcal{F}_1 = \mathcal{F}_3$ and $\mathcal{F}_2 = \mathcal{F}_3$, so $K_1 \cup K_2$ is compact.
+	$K_1$ and $K_2$ are compact, so let $\mathcal{U}_3$ be an open cover of $K_3 = K_1 \cup K_2$.
+So let $\mathcal{U}_1 = \mathcal{U}_3 \supseteq K_1$ and $\mathcal{U}_2 = \mathcal{U}_3 \supseteq K_2$.
+Since $K_1, K_2$ are compact choose finite $\mathcal{F}_1 \subseteq \mathcal{U}_1 = \mathcal{U}_3$ and $\mathcal{F}_2 \subseteq \mathcal{U}_2 = \mathcal{U}_3$, so $\bigcup \mathcal{F}_1 \supseteq K_1$ and $\bigcup \mathcal{F}_2 \supseteq K_2$ and $\bigcup (\mathcal{F}_1 \cup \mathcal{F}_2) \supseteq K_3$.
 	\end{proof}
@@
 	\begin{proof}
-	For $F = \lbrace x_i : 0 \leq x_i < n \rbrace \subseteq \mathbb{X}$, let $\mathcal{U}$ be an open covering on $F$ so $\bigcup \mathcal{U} \supseteq F$.
-Then we can find  a finite $\mathcal{F} \subseteq \mathcal{U}$ such that $\bigcup \mathcal{F} \supseteq F$.
-Suppose $\mathcal{U}_0 = \lbrace x_0 : -1 \leq x_0 < n+1 \rbrace \subseteq \mathcal{U}$ then let $\mathcal{F} = \mathcal{U}_0$, so $\bigcup \mathcal{F} \supseteq F$.
+	For $F = \lbrace x_i : 0 \leq x_i < n \rbrace \subseteq \mathbb{X}$, let $\mathcal{U}$ be an open covering of $F$ so $\bigcup \mathcal{U} \supseteq F$.
+For each $0 \leq i < n$, let $\mathcal{U}_i \in \mathcal{U}$ satisfy $x_i \in \mathcal{U}_i$.
+Let finite $\mathcal{F} = \lbrace x_i : x_i \in \mathcal{U}_i \rbrace$, so $\bigcup \mathcal{F} \supseteq F$ and $F$ is compact.
 	\end{proof}
@@
 	\begin{proof}
-	Let $K = \lbrace 0 \rbrace \cup \lbrace \frac{1}{n} : n \in \mathbb{Z^+} \rbrace \subseteq \mathbb{R}$ and let $\mathcal{U}$ be an open covering on $K$ such that $\bigcup \mathcal{U} \supseteq K$.
-So for $\mathcal{U}_0 \subseteq \mathcal{U}, \mathcal{U}_0 = \lbrace n_0 : -1 \leq n_0 \leq 2, n_0 \in \mathbb{Z} \rbrace$.
-$\bigcup \mathcal{U}_0 \supseteq K$.
-So, let finite $\mathcal{F} = \mathcal{U}_0$, so $\mathcal{F} \subseteq \mathcal{U}$ and $\mathcal{F} \supseteq K$.
+	Let $K = \lbrace 0 \rbrace \cup \lbrace \frac{1}{n} : n \in \mathbb{Z^+} \rbrace \subseteq \mathbb{R}$ and let $\mathcal{U}$ be an open covering of $K$.
+We may choose $U_0 \in \mathcal{U}$ where $0 \in U_0$.
+So pick $a<b \in \mathbb{R}$ where $0 \in (a, b) \subseteq U_0$.
+Now let finite $F = \lbrace \frac{1}{m} : 0 \leq m < n \rbrace$ so it is compact, and choose $\mathcal{F} \subseteq \mathcal{U}$ with $\bigcup \mathcal{F} \supseteq F \cup U_0$ so $K$ is compact.
 	\end{proof}
@@
 	\begin{proof}
-	For unbounded $K \subseteq \mathbb{R}$ suppose there is an open covering $\mathcal{U}$ on $K$.
-Then there exists a finite $\mathcal{F} \subseteq \mathcal{U}$ such that $\bigcup \mathcal{F} \supseteq K$.
-For $\mathcal{F}$ to be finite it must be bounded.
-So, there is no $\bigcup \mathcal{F} \supseteq K$.
-Essentially we would need $\mathcal{F} = \lbrace (- \infty , n) : n \in \mathbb{Z^-} \rbrace \cup \lbrace (n-3, \infty) : n \in \mathbb{Z^+} \rbrace$ which is not finite.
+	Let $\mathcal{U} = \lbrace (n-2, n) : n \in \mathbb{Z} \rbrace$.
+Let $n_i \in \mathbb{Z}$ be arbitrary for $0 \leq i < n$.
+Then $\mathcal{F} = \lbrace (n_i - 2, n_i) : 0 \leq i < n \rbrace$ is an arbitrary finite sub collection of $\mathcal{U}$.
+However, $\bigcup \mathcal{F} \not\supseteq K$, for $min(n_i-2: 0 \leq i < n)$ and $max(n_i : 0 \leq i < n)$ we can find a $k \in K : k < min(n_i-2: 0 \leq i < n)$ or $k > max(n_i : 0 \leq i < n)$.
 	\end{proof}

### 2018-04-10 project.tex
corrections
corrections and (a,b) in R is not compact

@@
 		\item See definition 6-2.
-		\item Let $U \in \tau$, then for every $B \subseteq U, B \in \mathcal{B}$.
-Let $\mathcal{B'} = \lbrace B : B \in \mathcal{B} \rbrace$ so $U = \bigcup \mathcal{B'}$.
-Now let $\mathcal{B'} \subseteq \mathcal{B}$ such that for each $B \in \mathcal{B}, B \in \mathcal{B'}$ so $\bigcup \mathcal{B'} = U$.
+		\item Let $U \in \tau$, then for every $x \in U$, there exists $B_x \in \mathcal{B}$ where $x \in B_x \subseteq U \in \tau$.
+Let $\mathcal{B'} = \lbrace B_x : B_x \in \mathcal{B} \rbrace$ so $U = \bigcup \mathcal{B'}$.
+Now let $\mathcal{B'} \subseteq \mathcal{B} \subseteq \tau$, and since $\mathcal{B'} \subseteq \tau, \bigcup \mathcal{B'} \in \tau$.
 		\end{enumerate}
@@
 		\item Now consider $B_1, B_2 \in \mathcal{B}$. $B_1 = \mathbb{X}$ and $B_2 = \mathbb{X}$ Let $x \in B_1 \cap B_2$, then $x \in B_3 = \mathbb{X} : B_1 \cap B_2 = \mathbb{X}$.
-		\item Choose $\mathcal{B}_\emptyset \subseteq \mathcal{B}$ and $\mathcal{B}_\mathbb{X} \subseteq \mathcal{B}$ where $\bigcup \mathcal{B}_\emptyset = \emptyset$ and $\bigcup \mathcal{B}_\mathbb{X} = \mathbb{X}$, so $\bigcup \mathcal{B} = \tau = \lbrace \emptyset, \mathbb{X} \rbrace$.
+		\item Choose $\mathcal{B}_\emptyset = \emptyset \subseteq \mathcal{B}$ and $\mathcal{B}_\mathbb{X} = \lbrace \mathbb{X} \rbrace \subseteq \mathcal{B}$ where $\bigcup \mathcal{B}_\emptyset = \emptyset$ and $\bigcup \mathcal{B}_\mathbb{X} = \mathbb{X}$, so since $\mathcal{P}(\mathcal{B}) = \lbrace \emptyset, \lbrace \mathbb{X} \rbrace \rbrace$, $\lbrace \bigcup \mathcal{B'} : \mathcal{B'} \subseteq \mathcal{B} \rbrace = \lbrace \bigcup \mathcal{B}_\emptyset, \bigcup \mathcal{B}_\mathbb{X} \rbrace = \tau = \lbrace \emptyset, \lbrace \mathbb{X} \rbrace \rbrace$.
 	\end{enumerate}
@@
 			\item Let $B_1, B_2 \in \mathcal{B}$. Let $y \in B_1 \cap B_2$. Let $B_3 = \lbrace y \rbrace$ $y \in B_3 = \lbrace y \rbrace \subseteq B_1 \cap B_2$. 
-			\item For every $x \in \mathbb{X}$ there are $B_x \in \mathcal{B}$ so $\bigcup \mathcal{B} = \bigcup \lbrace x : x \in \mathbb{X} \rbrace = \tau = \mathcal{P}(\mathbb{X})$.
+			\item Let $U \in \tau = \mathcal{P} \lbrace \mathbb{X} \rbrace$.
+Then $U = \lbrace x : x \in U \rbrace = \bigcup \lbrace x \rbrace = \bigcup \mathcal{B}_U$ for $\mathcal{B}_U = \lbrace \lbrace x \rbrace : x \in U \rbrace \subseteq \mathcal{B}$.
+			\item Let $\mathcal{B'} \subseteq \mathcal{B}$. Then $\bigcup \mathcal{B'} \in \mathcal{P}(\mathbb{X}) \in \tau$.
 		\end{enumerate}
@@
 	$K_1$ and $K_2$ are compact, so let $\mathcal{U}_3$ be an open cover of $K_3 = K_1 \cup K_2$.
-So let $\mathcal{U}_1 = \mathcal{U}_3 \supseteq K_1$ and $\mathcal{U}_2 = \mathcal{U}_3 \supseteq K_2$.
+So let $\mathcal{U}_1 = \mathcal{U}_3, \bigcup \mathcal{U}_3 \supseteq K_1$ and $\mathcal{U}_2 = \mathcal{U}_3, \bigcup \mathcal{U}_3 \supseteq K_2$.
 Since $K_1, K_2$ are compact choose finite $\mathcal{F}_1 \subseteq \mathcal{U}_1 = \mathcal{U}_3$ and $\mathcal{F}_2 \subseteq \mathcal{U}_2 = \mathcal{U}_3$, so $\bigcup \mathcal{F}_1 \supseteq K_1$ and $\bigcup \mathcal{F}_2 \supseteq K_2$ and $\bigcup (\mathcal{F}_1 \cup \mathcal{F}_2) \supseteq K_3$.
+Since $\mathcal{F}_1 \cup \mathcal{F}_2$ is a finite subset of $\mathcal{U}_3, K_3$ is compact.
 	\end{proof}
@@
 	\begin{proof}
-	For $F = \lbrace x_i : 0 \leq x_i < n \rbrace \subseteq \mathbb{X}$, let $\mathcal{U}$ be an open covering of $F$ so $\bigcup \mathcal{U} \supseteq F$.
+	For $F = \lbrace x_i : 0 \leq i < n \rbrace \subseteq \mathbb{X}$, let $\mathcal{U}$ be an open covering of $F$ so $\bigcup \mathcal{U} \supseteq F$.
 For each $0 \leq i < n$, let $\mathcal{U}_i \in \mathcal{U}$ satisfy $x_i \in \mathcal{U}_i$.
-Let finite $\mathcal{F} = \lbrace x_i : x_i \in \mathcal{U}_i \rbrace$, so $\bigcup \mathcal{F} \supseteq F$ and $F$ is compact.
+Let finite $\mathcal{F} = \lbrace U_i : 0 \leq i < n \rbrace \subseteq \mathcal{U}$, so $\bigcup \mathcal{F} \supseteq F$ and $F$ is compact.
 	\end{proof}
@@
 So pick $a<b \in \mathbb{R}$ where $0 \in (a, b) \subseteq U_0$.
-Now let finite $F = \lbrace \frac{1}{m} : 0 \leq m < n \rbrace$ so it is compact, and choose $\mathcal{F} \subseteq \mathcal{U}$ with $\bigcup \mathcal{F} \supseteq F \cup U_0$ so $K$ is compact.
+Let $N \in \mathbb{Z}^+$ where $0 < \frac{1}{N} < b$.
+Now let finite $F = \lbrace \frac{1}{m} : 1 \leq m < N \rbrace$ so it is compact, and choose $\mathcal{F} \subseteq \mathcal{U}$ with $\bigcup \mathcal{F} \supseteq F$.
+So $K = \lbrace \frac{1}{n} : n \in \mathbb{Z}^+$ and $n \geq N \rbrace$.
+$\bigcup n \in \mathbb{Z}_+$ and $\lbrace \frac{1}{n} : 1 \leq n < N \rbrace$ is covered by $\lbrace U_0 \rbrace \cup \mathcal{F}$.
 	\end{proof}
@@
 	\begin{proof}
+	Let $K$ be an unbounded subset of $\mathbb{R}$.
 Let $\mathcal{U} = \lbrace (n-2, n) : n \in \mathbb{Z} \rbrace$.
@@
 Then $\mathcal{F} = \lbrace (n_i - 2, n_i) : 0 \leq i < n \rbrace$ is an arbitrary finite sub collection of $\mathcal{U}$.
-However, $\bigcup \mathcal{F} \not\supseteq K$, for $min(n_i-2: 0 \leq i < n)$ and $max(n_i : 0 \leq i < n)$ we can find a $k \in K : k < min(n_i-2: 0 \leq i < n)$ or $k > max(n_i : 0 \leq i < n)$.
+However, $\bigcup \mathcal{F} \not\supseteq K$, for $min(n_i-2: 0 \leq i < n)$ and $max(n_i : 0 \leq i < n)$ we can find a $k \in K : k < min(n_i-2: 0 \leq i < n)$ or $k > max(n_i : 0 \leq i < n)$, so $k  \not\in \bigcup \mathcal{F}$ and $K$ is not compact.
 	\end{proof}
@@
 	\begin{proof}
+	Let $K = (a, b) \subseteq \mathbb{R}$, Let $\mathcal{U} = \lbrace (x, y) : x, y \in \mathbb{R}, a \leq x < y \leq b \rbrace$.
+So, $\bigcup \mathcal{U} \supseteq K$, and $\bigcup \mathcal{U} = K$.
+Let $n \in \mathbb{Z}$, let $x_i, y_i \in \mathbb{R}$ be arbitrary with $0 \leq i < n$.
+Then, $\mathcal{F} = \lbrace (x_i, y_i) : 0 \leq i < n \rbrace$ is an arbitrary finite subset of $\mathcal{U}$.
+However $\mathcal{F} \not\supseteq K$, for $min(x_i : 0 \leq i < n)$ and $max(y_i : 0 \leq i < n)$ we can find a $k \in K : k < min(x_i : 0 \leq i < n)$ or $k > max(y_i : 0 \leq i < n)$ so $k \not\in \bigcup \mathcal{F}$ and $K$ is not compact.
 	\end{proof}

### 2018-04-19 project.tex
Update
Sigma->Lindelof
Corrections

@@
 		\item Let $\mathcal{B} = \lbrace\mathbb{X}\rbrace$ and let $x \in \mathbb{X} = B \in \mathcal{B}$.
-		\item Now consider $B_1, B_2 \in \mathcal{B}$. $B_1 = \mathbb{X}$ and $B_2 = \mathbb{X}$ Let $x \in B_1 \cap B_2$, then $x \in B_3 = \mathbb{X} : B_1 \cap B_2 = \mathbb{X}$.
+		\item Now consider $B_1, B_2 \in \mathcal{B}$. $B_1 = \mathbb{X}$ and $B_2 = \mathbb{X}$ Let $x \in B_1 \cap B_2$, then $x \in B_3 \subseteq B_1 \cap B_2$.
 		\item Choose $\mathcal{B}_\emptyset = \emptyset \subseteq \mathcal{B}$ and $\mathcal{B}_\mathbb{X} = \lbrace \mathbb{X} \rbrace \subseteq \mathcal{B}$ where $\bigcup \mathcal{B}_\emptyset = \emptyset$ and $\bigcup \mathcal{B}_\mathbb{X} = \mathbb{X}$, so since $\mathcal{P}(\mathcal{B}) = \lbrace \emptyset, \lbrace \mathbb{X} \rbrace \rbrace$, $\lbrace \bigcup \mathcal{B'} : \mathcal{B'} \subseteq \mathcal{B} \rbrace = \lbrace \bigcup \mathcal{B}_\emptyset, \bigcup \mathcal{B}_\mathbb{X} \rbrace = \tau = \lbrace \emptyset, \lbrace \mathbb{X} \rbrace \rbrace$.
@@
 			\item Let $B_1, B_2 \in \mathcal{B}$. Let $y \in B_1 \cap B_2$. Let $B_3 = \lbrace y \rbrace$ $y \in B_3 = \lbrace y \rbrace \subseteq B_1 \cap B_2$. 
-			\item Let $U \in \tau = \mathcal{P} \lbrace \mathbb{X} \rbrace$.
-Then $U = \lbrace x : x \in U \rbrace = \bigcup \lbrace x \rbrace = \bigcup \mathcal{B}_U$ for $\mathcal{B}_U = \lbrace \lbrace x \rbrace : x \in U \rbrace \subseteq \mathcal{B}$.
-			\item Let $\mathcal{B'} \subseteq \mathcal{B}$. Then $\bigcup \mathcal{B'} \in \mathcal{P}(\mathbb{X}) \in \tau$.
+			\item Let $U \in \tau = \mathcal{P} ( \mathbb{X} )$.
+Then $U = \lbrace x : x \in U \rbrace = \bigcup \lbrace x : x \in U \rbrace = \bigcup \mathcal{B}_U$ for $\mathcal{B}_U = \lbrace \lbrace x \rbrace : x \in U \rbrace \subseteq \mathcal{B}$.
+			\newline Let $\mathcal{B'} \subseteq \mathcal{B}$. Then $\bigcup \mathcal{B'} \in \mathcal{P}(\mathbb{X}) \in \tau$.
 		\end{enumerate}
@@
 	For $F = \lbrace x_i : 0 \leq i < n \rbrace \subseteq \mathbb{X}$, let $\mathcal{U}$ be an open covering of $F$ so $\bigcup \mathcal{U} \supseteq F$.
-For each $0 \leq i < n$, let $\mathcal{U}_i \in \mathcal{U}$ satisfy $x_i \in \mathcal{U}_i$.
+For each $0 \leq i < n$, let $U_i \in \mathcal{U}$ satisfy $x_i \in U_i$.
 Let finite $\mathcal{F} = \lbrace U_i : 0 \leq i < n \rbrace \subseteq \mathcal{U}$, so $\bigcup \mathcal{F} \supseteq F$ and $F$ is compact.
@@
 Now let finite $F = \lbrace \frac{1}{m} : 1 \leq m < N \rbrace$ so it is compact, and choose $\mathcal{F} \subseteq \mathcal{U}$ with $\bigcup \mathcal{F} \supseteq F$.
-So $K = \lbrace \frac{1}{n} : n \in \mathbb{Z}^+$ and $n \geq N \rbrace$.
-$\bigcup n \in \mathbb{Z}_+$ and $\lbrace \frac{1}{n} : 1 \leq n < N \rbrace$ is covered by $\lbrace U_0 \rbrace \cup \mathcal{F}$.
+So $K = \lbrace 0 \rbrace \cup \lbrace \frac{1}{m} : N \leq m < \infty \rbrace \cup \lbrace \frac{1}{m} : 1 \leq m < N \rbrace$.
 	\end{proof}
@@
 	\begin{proof}
-	Let $K = (a, b) \subseteq \mathbb{R}$, Let $\mathcal{U} = \lbrace (x, y) : x, y \in \mathbb{R}, a \leq x < y \leq b \rbrace$.
+	Let $K = (a, b) \subseteq \mathbb{R}$, Let $\mathcal{U} = \lbrace (x, y) : x, y \in \mathbb{R}, a < x < y < b \rbrace$.
 So, $\bigcup \mathcal{U} \supseteq K$, and $\bigcup \mathcal{U} = K$.
@@
 Then, $\mathcal{F} = \lbrace (x_i, y_i) : 0 \leq i < n \rbrace$ is an arbitrary finite subset of $\mathcal{U}$.
-However $\mathcal{F} \not\supseteq K$, for $min(x_i : 0 \leq i < n)$ and $max(y_i : 0 \leq i < n)$ we can find a $k \in K : k < min(x_i : 0 \leq i < n)$ or $k > max(y_i : 0 \leq i < n)$ so $k \not\in \bigcup \mathcal{F}$ and $K$ is not compact.
+However $\bigcup \mathcal{F} \not\supseteq K$, for $min(x_i : 0 \leq i < n)$ we can find a $k \in K : k < min(x_i : 0 \leq i < n)$ which is greater than $a$ so $k \not\in \bigcup \mathcal{F}$ and $K$ is not compact.
 	\end{proof}
@@
 	  \(K=\bigcup_{n\in\mathbb N} K_n\).
+	  \newline \newline
 	\end{definition}
-
 	\begin{theorem}
@@
 	\begin{proof}
+	Let $K$ be \(\sigma\)-compact.
+Let $\mathcal{U}$ be an arbitrary collection of open sets such that $\bigcup \mathcal{U} \supseteq K$.
+Choose finite $\mathcal{F} = \lbrace F_i : i \in \mathbb{N} \rbrace \subseteq \mathcal{U}$ so $\mathcal{F}$ is countable.
+Let each $F_{i \in \mathbb{N}} \supseteq K_{n \in \mathbb{N}}$ so, $\bigcup \mathcal{F} = \bigcup_{i \in \mathbb{N}} F_i \supseteq \bigcup_{n \in \mathbb{N}} K_n = K$.
+Therefore $\bigcup \mathcal{F} \supseteq K$.
+
 	\end{proof}

### 2018-04-24 project.tex
Compact Point => Lindelof
two possible proofs for GRU_K,P(X) => Lindelof

Corrections made to sigma-compact => lindelof

@@
 Now let finite $F = \lbrace \frac{1}{m} : 1 \leq m < N \rbrace$ so it is compact, and choose $\mathcal{F} \subseteq \mathcal{U}$ with $\bigcup \mathcal{F} \supseteq F$.
-So $K = \lbrace 0 \rbrace \cup \lbrace \frac{1}{m} : N \leq m < \infty \rbrace \cup \lbrace \frac{1}{m} : 1 \leq m < N \rbrace$.
+So, $\lbrace \bigcup \mathcal{F} \cup (a,b) \cup U_0 \rbrace \supseteq K$.
 	\end{proof}
@@
 	Let $K$ be \(\sigma\)-compact.
-Let $\mathcal{U}$ be an arbitrary collection of open sets such that $\bigcup \mathcal{U} \supseteq K$.
-Choose finite $\mathcal{F} = \lbrace F_i : i \in \mathbb{N} \rbrace \subseteq \mathcal{U}$ so $\mathcal{F}$ is countable.
-Let each $F_{i \in \mathbb{N}} \supseteq K_{n \in \mathbb{N}}$ so, $\bigcup \mathcal{F} = \bigcup_{i \in \mathbb{N}} F_i \supseteq \bigcup_{n \in \mathbb{N}} K_n = K$.
-Therefore $\bigcup \mathcal{F} \supseteq K$.
+Let $\mathcal{F}_n = \lbrace U_{n0}, U_{n1}, ..., U_{nm} \rbrace$ be a finite subcover of $\mathcal{U}$ for $K_n$.
+So, $\mathcal{C} = \bigcup_{n \in \mathbb{N}} \mathcal{F}_n$ is a countable subcover of $\mathcal{U}$ for $K$.
+Therefore $K$ is Lindel\"of.
 
@@
 
+	\begin{theorem}
+		If $\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{K, P} (X)$ then $X$ is Lindel\"of.
+	\end{theorem}
+	\begin{proof}
+	 It is shown in Theorem 2.5 (3, Clontz) that when $\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{K, P} (X)$, $X$ is hemicompact and furthermore by the definition of hemicompactness  $X = \lbrace \bigcup_{m \leq n} \sigma (m) : n < \omega \rbrace$.
+	 \newline\newline
+	 For $X = \lbrace \bigcup_{m \leq n} \sigma (m) : n < \omega \rbrace$, let $\mathcal{U}$ be an arbitrary covering of $X$ and let $\mathcal{F}_n = \lbrace U_{n0}, U_{n2}, ...
+, U_{nm}\rbrace$ be a finite subcover of $\mathcal{U}$ for $K_n$.
+So, $\mathcal{C} = \bigcup_{n \in \mathbb{N}} \mathcal{F}_n$ is a countable subcover of of $\mathcal{U}$ for $K$.\newline \newline
+	 Alternate idea:
+	 \newline
+	 For $X = \lbrace \bigcup_{m \leq n} \sigma (m) : n < \omega \rbrace$, let $\mathcal{U}$ be an arbitrary covering of $X$ and let $\mathcal{F} \subseteq \mathcal{U}$, with $\mathcal{F} = \lbrace F_i : i < \omega \rbrace$.
+For each $\sigma(m)$ with $m \leq n < \omega$ let $F_{i < \omega} \supseteq \sigma(m)$.
+So, $\bigcup \mathcal{F} \supseteq \lbrace \bigcup_{m \leq n} \sigma(m) : n < \omega \rbrace$ so $X$ is Lindel\"of.
+	\end{proof}
 \end{document}

### 2018-04-25 article.tex
add minimal article file for Cody

\documentclass{amsart}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

      \theoremstyle{plain}
      \newtheorem{theorem}{Theorem}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{conjecture}[theorem]{Conjecture}
      \newtheorem{question}[theorem]{Question}
      \newtheorem{claim}[theorem]{Claim}

      \theoremstyle{definition}
      \newtheorem{definition}[theorem]{Definition}
      \newtheorem{notation}[theorem]{Notation}
      \newtheorem{example}[theorem]{Example}
      \newtheorem{game}[theorem]{Game}

      \theoremstyle{remark}
      \newtheorem{remark}[theorem]{Remark}

\begin{document}

\title{Relating games of Menger, countable fan tightness, and selective separability}

\author{Steven Clontz}
\address{Department of Mathematics and Statistics,
The University of South Alabama,
Mobile, AL 36688}
\email{sclontz@southalabama.edu}

\begin{abstract}
  By adapting techniques of Arhangel'skii, Barman, and Dow, we may
  equate the existence of perfect-information, Markov, and tactical
  strategies between two interesting selection games.
  These results shed some light on Gruenhage's question asking whether all
  strategically selectively separable spaces are Markov selectively
  separable.
\end{abstract}

\maketitle

\section{Introduction}

\begin{definition}
  Foo
\end{definition}

Bar.

\begin{question}\label{mainQuestion}
  Does \(SS^+\) imply \(SS^{++}\)?
\end{question}

\section{\(CFT\), \(CDFT\) and \(SS\)}

\begin{theorem}[Lemma 2.7 of ]
  The following are equivalent for any topological space \(X\).
  \begin{itemize}
    \item \(X\) is \(SS\).
    \item \(X\) is separable and \(CDFT\).
    \item \(X\) has a countable dense subset \(D\) where
          \(CDFT_x\) holds for all \(x\in D\).
  \end{itemize}
\end{theorem}

\end{document}

### 2018-04-30 project.tex
Update

--- 2018-04-19 project.tex
@@
 	\begin{definition}
-	  A subset \(K\) of a topological space \(X\) is said to be \textbf{\(\sigma\)-compact} if
+	  A subset \(K\) of a topological space \(X\) is said to be \textbf{\(\boldsymbol{\sigma}\)-compact} if
 	  there exist compact subspaces \(K_n\) of \(X\) for \(n\in\mathbb N\) such that
@@
 	\begin{theorem}
-		Every \(\sigma\)-compact subset of a topological space is Lindel\"of.
+		Every \(\boldsymbol{\sigma}\)\textbf{-compact} subset of a topological space is \textbf{Lindel\"of}.
 	\end{theorem}
@@
 	  A subset \(K\) of a topological space \(X\) is said to be \textbf{hemicompact} if
-	  there exist compact subspaces \(K_n\) of \(X\) for \(n\in\mathbb N\) such that
-	  \(K=\bigcup_{n\in\mathbb N} K_n\), and for every compact subset \(H\subseteq K\),
+	  for every compact subset \(H\subseteq K\),
 	  \(H\subseteq K_n\) for some \(n\in\mathbb N\).
@@
 	\begin{theorem}
-		Every hemicompact subset of a topological space is \(\sigma\)-compact.
+		Every \textbf{hemicompact} subset of a topological space is \(\boldsymbol{\sigma}\)\textbf{-compact}.
 	\end{theorem}
 	\begin{proof}
-		This proof is trivial as it is defined as stated here in definition 21.
+		For all compact $C \subseteq K \subseteq X$, $C \subseteq K_{n \in \mathbb{N}} \subseteq K$. \newline
+		$K_{n \in \mathbb{N}} \subseteq X$.
+Since all compact $C_{i \in \mathbb{N}}$ are subsets of some $K_{n \in \mathbb{N}}$, $\underset{n \in \mathbb{N}}{\bigcup}K_n \supseteq \underset{i \in \mathbb{N}}{\bigcup} C_i$ so $\underset{n\in\mathbb{N}}{\bigcup}K_n = K$.
 	\end{proof}
 
+	\begin{definition}
+		$X$ is \textbf{locally compact} if for every $x \in X$ there exists an open set $U$ and compact $K$ with $x \in U \subseteq K$.
+	\end{definition}
+
+	\begin{definition}
+		$x$ is a \textbf{cluster point} of $\langle p_n \rangle_{n < \omega}$ if and only if for every neighborhood $U$ of $x$, $U$ hits infinitely many $p_n$.
+	\end{definition}
+
+	\begin{definition}
+		$\boldsymbol{Gru_{\mathcal{K},\mathcal{P}}(X)}$ is a game defined as... $\mathcal{K}$ wins if and only if $\langle p_n \rangle_{n<\omega}$ lacks a \textbf{cluster point}. 
+	\end{definition}
+
+	\begin{definition}
+	$\boldsymbol{\mathcal{K} \underset{pre}{\uparrow} Gru_{\mathcal{K}, \mathcal{P}}(X)}$ is the statement that $\mathcal{K}$ has a winning strategy $\sigma : \omega \rightarrow \mathcal{K}(X)$ that depends only on the round number (ignores the moves of $\mathcal{P}$).
+	\end{definition}
+
+	\begin{theorem}
+		If $X$ is \textbf{Lindel\"of}, then $\boldsymbol{\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)}$
+	\end{theorem}
+	\begin{proof}
+		Let $X$ be Lindel\"of, so there is a countable subcollection $\mathcal{C} \subseteq \mathcal{U}$, where $\mathcal{U}$ is an arbitrary covering of $X$.
+So, $\mathcal{C} = \lbrace U_n : U_n \in \mathcal{U}, n < \omega \rbrace$ and $\bigcup \mathcal{C} \supseteq X$.\newline \newline
+		For $Gru_{\mathcal{K}, \mathcal{P}}(X)$, $\mathcal{K}$ chooses compact $K_{i \leq n < \omega} \supseteq U_{n < \omega} \in \mathcal{C}$ and $\mathcal{P}$ chooses $p \in X$ such that $p \not\in K_{i \leq n < \omega}$.
+Since $\lbrace K_i : i \leq n < \omega \rbrace$ is countable and $\bigcup \lbrace K_i : i \leq n < \omega \rbrace \supseteq X$, $\mathcal{P}$ has countably many $p_{m \leq n < \omega}$.
+Therefore $\langle p_m \rangle$ is finite and $X$ has no cluster points.
+Thus, $\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)$.
+	\end{proof}
+
+	\begin{lemma}
+	Let $K$ be a compact subset of $X$. If $\langle p_n \rangle$ is a sequence of points in $K$, then $\langle p_n \rangle$ has a cluster point.
+	\end{lemma}
+	\begin{proof}
+	This is obviously true if the sequence only uses finitely many different points (one point must be repeated infinitely often, so it is its own cluster point).
+So assume $\langle p_n \rangle$ uses infinitely many different points.
+If $\langle p_n \rangle$ didn't have a cluster point, then for each $x \in K$, let $U_x$ contain only finitely many $p_n$.
+$\lbrace U_x : x \in K \rbrace$ covers $K$, so choose $x_i$ for $i \leq n : \lbrace U_{x_i} : i \leq n \rbrace$ covers $K$.
+But each $U_{x_i}$ contains only finitely many $p_n$, so $\langle p_n \rangle$ cannot have infinitely many different points to choose from and $\langle p_n \rangle$ does not have a cluster point.
+	\end{proof}
+
+	\begin{theorem}
+		$\boldsymbol{\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)} \Rightarrow X$ is \textbf{hemicompact}.
+	\end{theorem}
+	\begin{proof}
+		We prove the contrapositive.
+Let $\sigma$ be a predetermined strategy, and assume $X$ isn't hemicompact.
+So there exists a compact $K$ that isn't a union of finite $\sigma(n)$, so player $\mathcal{P}$ may always legally choose a point $p_n \in K$.
+Then by the lemma, $\langle p_n \rangle$ has a cluster point.
+Therefore $\sigma$ isn't a winning strategy.
+	\end{proof}
 \end{document}

### 2018-05-02 article.tex
Update - Article

@@
 
-\title{Relating games of Menger, countable fan tightness, and selective separability}
+\title{An Investigation in Topological Properties}
 
-\author{Steven Clontz}
-\address{Department of Mathematics and Statistics,
-The University of South Alabama,
-Mobile, AL 36688}
-\email{sclontz@southalabama.edu}
+\author{Cody Martin}
+\address{1313 Schillinger Rd. S. 
+Apt. 3407
+Mobile, AL 36695}
+\email{cdm1322@jagmail.southalabama.edu}
 
 \begin{abstract}
-  By adapting techniques of Arhangel'skii, Barman, and Dow, we may
-  equate the existence of perfect-information, Markov, and tactical
-  strategies between two interesting selection games.
-  These results shed some light on Gruenhage's question asking whether all
-  strategically selectively separable spaces are Markov selectively
-  separable.
+  This is the culmination of topics and topological properties that have been studied over the course of the Spring 2018 semester, mentored by Dr. Steven Clontz.
 \end{abstract}
@@
 
-\section{Introduction}
+\section{Basic Topological Properties and Definitions}
+
+	\begin{proposition}
+	Find an infinite collection of open intervals in $\mathbb{R}$ whose intersection is not an open interval.
+	\end{proposition}
+	\begin{proof}
+	$\bigcap\lbrace (\frac{-1}{n}, \frac{1}{n}) : n \in \mathbb{Z}^+\rbrace = \lbrace 0 \rbrace$ which is not an open interval or even open.
+	\end{proof}
+
+  \begin{proposition}
+      Any finite union of closed sets is closed, and any arbitrary intersection of closed sets is closed.
+  \end{proposition}
+  \begin{proof}
+	We proceed by showing that any finite union of closed sets is closed.
+Let C, D be closed sets.
+Let A, B be compliments of C, D so A, B are open.
+Then, A $\cap$ B is also open.
+Thus, X$\setminus$(A $\cap$ B) is closed.
+By Demorgan's Law, X$\setminus$(A $\cap$ B) = X$\setminus$A $\cup$ X$\setminus$B = C $\cup$ D which is closed.
+	\newline\newline Now that we've shown that C $\cup$ D is closed for all C, D; Assume C$_1$ $\cup $ C$_2 \cup ...$ $\cup $ C$_n$ is closed for closed sets C$_i$.
+Then for C$_1$ $\cup$ ...
+$\cup$ C$_n$ $\cup$ C$_{n+1}$, let K = C$_1$ $\cup$ ...
+$\cup$ C$_n$.
+Thus K $\cup$ C$_{n+1}$ = C$_1$ $\cup$ ...
+$\cup$ C$_n$ $\cup$ C$_{n+1}$ is closed.
+	\newline\newline Now we show that any arbitrary intersection of closed sets is closed.
+Let $\mathcal{C}$ be a collection of closed sets.
+Let $\mathcal{U} = \lbrace$X$\setminus$C : C $\in \mathcal{C}\rbrace$, so $\mathcal{U}$ is a collection of open sets.
+Then, $\bigcup \mathcal{U}$ is also open.
+Thus, X$\setminus\bigcup\mathcal{U}$ is closed.
+By Demorgan's Law, X$\setminus\bigcup\mathcal{U}$ = $\bigcap\mathcal{C}$ Therefore, $\bigcap\mathcal{C}$ is closed.
+	\end{proof}
+
+	\begin{lemma}
+	A set U is open if and only if for every point $x \in$ U, there exists an open set U$_x$ where $x \in $ U$_x \subseteq$ U
+	\end{lemma}
+	\begin{proof} Suppose U is open, then for all x $\in$ U there exists an open U$_x$ = U, such that x $\in$ U$_x \subseteq$ U.
+	\newline
+	To show the converse, suppose that for each x $\in$ U there is an open set U$_x$ where x $\in$ U$_x$ $\subseteq$ U.
+For $x \in U, x \in U_x$ so $x \in \bigcup \lbrace U_x : x \in U \rbrace$.
+Thus $U \subseteq \bigcup \lbrace U_x : x \in U_x \rbrace$.
+Now let y $\in$ U$_x$ for some x $\in$ U, then U$_x$ $\subseteq$ U.
+Thus U $\supseteq$ $\bigcup \lbrace$ U$_x$ : x $\in$ U $\rbrace$.
+Therefore U = $\bigcup \lbrace$ U$_x$ : x $\in$ U $\rbrace$.
+	\end{proof}
+
+	\begin{proposition}
+		A set K in a topological space X is closed if and only if K contains all its limit points.
+	\end{proposition}
+	\begin{proof} Suppose K contains all its limit points.
+	If K = X, then K is closed because $\emptyset$ is open.	Otherwise let x $\in$ X$\setminus$K, so x is not a limit point of K.	Then, $\exists$ $x \in$ U$_x \in \tau$ such that U$_x \cap$ K = $\emptyset$ since $x \not\in K$.	So, $x \in $ U$_x \subseteq$ X$\setminus$K.	By the lemma, X$\setminus$K is open so K is closed.
+
+	To show the converse is true as well, let x $\in$ X$\setminus$K, which is an open set by the lemma.
+Since $($X$\setminus$K$)\cap$K is the empty set, x is not a limit point of K.
+So, if $\ell$ is any limit point of K, then $\ell \not\in$ X$\setminus$K, so $\ell \in$ K and K contains all of its limit points.
+	\end{proof}
+
+	\begin{proposition}
+	Verify the discrete and indiscrete topologies are topologies
+	\end{proposition}
+	\begin{proof} To prove the discrete topology is an actual topology, first we define that the discrete topology on a set X is $\tau$ = $\mathcal{P}($X$)$.	$\emptyset$, X $\in \mathcal{P}($X$)$, So $\emptyset,$ X $\in \tau$.
+Now, let $\mathcal{U} \subseteq \tau$ = $\mathcal{P}($X$)$, then the $\bigcup$U $\in \mathcal{P}($X$)$.
+Let U, V $\in \tau$ = $\mathcal{P}($X$)$ then the intersection U $\cap$ V $\in \mathcal{P}($X$)$ = $\tau$.
+Now to show that the indiscrete topology is an actual topology, we define that the indiscrete topology on a set X is given as $\tau$ = $\lbrace \emptyset$, X$\rbrace$.
+Clearly, $\emptyset$, X $\in \tau$.
+Let $\mathcal{U}$ be a collection of open sets in X, then $\bigcup \mathcal{U}$ = X, thus $\bigcup \mathcal{U} \in \tau$.
+	\end{proof}
 
 	\begin{definition}
-  Foo
+		A collection of sets \(\mathcal{B}\subseteq\mathcal{P}(X)\) is
+		called a \textbf{basis} if:
+		\begin{enumerate}
+			\item For all \(x\in X\), there exists \(B\in\mathcal{B}\) such that
+			\(x\in B\).
+			\item  For all \(B_1,B_2 \in \mathcal{B}\) with \(x \in B_1 \cap B_2\), there exists \(B_3 \in \mathcal{B}\) with
+			\(x\in B_3 \subseteq B_1 \cap B_2\).
+		\end{enumerate}
+	  The set \(\{\bigcup\mathcal{B}':\mathcal{B}'\subseteq\mathcal{B}\}\)
+		is called the topology generated by \(\mathcal{B}\).
 	\end{definition}
 
-Bar.
+	\begin{theorem}
+		The ``topology generated by \(\mathcal{B}\)'' is actually a topology.
+	\end{theorem}
+	\begin{proof} 
+	This was not finished correctly and fell through the cracks of time. Should it be removed?
+	\end{proof}
 
-\begin{question}\label{mainQuestion}
-  Does \(SS^+\) imply \(SS^{++}\)?
-\end{question}
+	\begin{theorem}
+	Let $\tau$ be a topology on X. Then $\mathcal{B} \subseteq \tau$ generates $\tau$ if:
+	\newline
+	1. For all x $\in$ U $\in \tau$, there exists B $\in$ $\mathcal{B}$ where x $\in$ B $\subseteq$ U $\in \tau$
+	\newline
+	2. For all B$_1$, B$_2 \in \mathcal{B}$ with x $\in ($B$_1 \cap$ B$_2)$, there exists B$_3 \in \mathcal{B}$ with x $\in$ B$_3 \subseteq$ B$_1 \cap$ B$_2$.
+\end{theorem}
+\begin{proof}:\newline
+	\begin{enumerate}
+		\item For $x \in \mathbb{X} \in \tau$, select $x \in B \subseteq \mathbb{X} \in \tau$, so 1 of definition 6 holds.
+		\item See definition 6-2.
+		\item Let $U \in \tau$, then for every $x \in U$, there exists $B_x \in \mathcal{B}$ where $x \in B_x \subseteq U \in \tau$.
+Let $\mathcal{B'} = \lbrace B_x : B_x \in \mathcal{B} \rbrace$ so $U = \bigcup \mathcal{B'}$.
+Now let $\mathcal{B'} \subseteq \mathcal{B} \subseteq \tau$, and since $\mathcal{B'} \subseteq \tau, \bigcup \mathcal{B'} \in \tau$.
+		\end{enumerate}
+\end{proof}
 
-\section{\(CFT\), \(CDFT\) and \(SS\)}
+	\begin{theorem}
+	$\lbrace\mathbb{X}\rbrace$ is a basis for $\tau$ = $\lbrace\emptyset$, $\mathbb{X}\rbrace$. (indiscrete)
+	\end{theorem}
+	\begin{proof}:\newline
+	\begin{enumerate}
+		\item Let $\mathcal{B} = \lbrace\mathbb{X}\rbrace$ and let $x \in \mathbb{X} = B \in \mathcal{B}$.
+		\item Now consider $B_1, B_2 \in \mathcal{B}$. $B_1 = \mathbb{X}$ and $B_2 = \mathbb{X}$ Let $x \in B_1 \cap B_2$, then $x \in B_3 \subseteq B_1 \cap B_2$.
+		\item Choose $\mathcal{B}_\emptyset = \emptyset \subseteq \mathcal{B}$ and $\mathcal{B}_\mathbb{X} = \lbrace \mathbb{X} \rbrace \subseteq \mathcal{B}$ where $\bigcup \mathcal{B}_\emptyset = \emptyset$ and $\bigcup \mathcal{B}_\mathbb{X} = \mathbb{X}$, so since $\mathcal{P}(\mathcal{B}) = \lbrace \emptyset, \lbrace \mathbb{X} \rbrace \rbrace$, $\lbrace \bigcup \mathcal{B'} : \mathcal{B'} \subseteq \mathcal{B} \rbrace = \lbrace \bigcup \mathcal{B}_\emptyset, \bigcup \mathcal{B}_\mathbb{X} \rbrace = \tau = \lbrace \emptyset, \lbrace \mathbb{X} \rbrace \rbrace$.
+	\end{enumerate}
+	\end{proof}
 
-\begin{theorem}[Lemma 2.7 of ]
-  The following are equivalent for any topological space \(X\).
-  \begin{itemize}
-    \item \(X\) is \(SS\).
-    \item \(X\) is separable and \(CDFT\).
-    \item \(X\) has a countable dense subset \(D\) where
-          \(CDFT_x\) holds for all \(x\in D\).
-  \end{itemize}
+	\begin{theorem}
+	$\mathcal{B} = \lbrace\lbrace x \rbrace$ : x $\in \mathbb{X}\rbrace$ is a basis for $\tau$ = $\mathcal{P}(\mathbb{X})$ = $\lbrace$ U : U $\subseteq \mathbb{X} \rbrace$. (discrete)
+	\end{theorem}
+	\begin{proof}:\newline
+		\begin{enumerate}
+			\item Let $x \in U \in \tau = \mathcal{P}(\mathbb{X})$. Then for $B = \lbrace x \rbrace \in \mathcal{B}, x \in B \subseteq U$.
+			\item Let $B_1, B_2 \in \mathcal{B}$. Let $y \in B_1 \cap B_2$. Let $B_3 = \lbrace y \rbrace$ $y \in B_3 = \lbrace y \rbrace \subseteq B_1 \cap B_2$. 
+			\item Let $U \in \tau = \mathcal{P} ( \mathbb{X} )$.
+Then $U = \lbrace x : x \in U \rbrace = \bigcup \lbrace x : x \in U \rbrace = \bigcup \mathcal{B}_U$ for $\mathcal{B}_U = \lbrace \lbrace x \rbrace : x \in U \rbrace \subseteq \mathcal{B}$.
+			\newline Let $\mathcal{B'} \subseteq \mathcal{B}$. Then $\bigcup \mathcal{B'} \in \mathcal{P}(\mathbb{X}) \in \tau$.
+		\end{enumerate}
+	\end{proof}
+
+	\begin{definition}
+	The \textbf{Euclidean topology} on $\mathbb{R}$ is the topology generated by the \textbf{basis} \newline $\lbrace(a, b) : a < b \in \mathbb{R}\rbrace$.
+	\end{definition}
+
+	\begin{theorem}
+	$\lbrace($a, b$)$ : a $<$ b $\in \mathbb{R}\rbrace$ is a basis.
+	\end{theorem}
+	\begin{proof}:\newline
+		\begin{enumerate}
+			\item Let $\mathcal{B} = \lbrace (a, b) : a < b \in \mathbb{R} \rbrace$. Let $x \in \mathbb{R}$ and let $B = (x-1, x+1)$, then $x \in B \subseteq \mathbb{R}$ and $B \in \mathcal{B}$.	
+			\item For $B_1 = (a_1, b_1)$, $B_2 = (a_2, b_2)$, $a_1<b_1$, $a_2<b_2 \in \mathbb{R}$ with $x \in B_1 \cap B_2$, then there is $B_3 = ( max(a_1, a_2), min(b_1, b_2) ) \subseteq B_1 \cap B_2$ such that $a_1,a_2<x<b_1,b_2$ so $ x \in B_3$.
+		\end{enumerate}
+	\end{proof}
+
+	\begin{theorem}
+	$\lbrace($a, b$)$ : a $<$ b $\in \mathbb{Q}\rbrace$ is a basis for the Euclidean topology.
+	\end{theorem}
+	\begin{proof}:\newline
+		\begin{enumerate}
+		\item Let $\mathcal{B} = \lbrace (a, b) : a < b \in \mathbb{Q}\rbrace$ Let $x \in \mathbb{R}$ then, $\lfloor x \rfloor -1 < x < \lceil x \rceil + 1$.
+Let B = $(\lfloor x \rfloor -1, \lceil x \rceil + 1)$, so $x \in B \in \mathcal{B}$ and $B \subseteq \mathbb{Q}$.
+		\item Now, for $B_1, B_2 \in \mathcal{B}, \exists x \in B_1 \cap B_2 : x \in B_1$ and $x \in B_2$.
+$a_1, a_2 < b_1, b_2 \in \mathbb{Q}.$ Let $B_1 = (a_1, b_1)$ and $B_2 = (a_2, b_2)$.
+Now let $B_3 = (max(a_1,a_2), min(b_1,b_2))$ with $a_1,a_2<x<b_1,b_2$ so $x \in B_3$.
+So, $x \in B_3 \subseteq B_1 \cap B_2$.
+		\item Now show it generates $\tau$...
+		\end{enumerate} 
+	\end{proof}
+
+\section{Compactness Properties}
+
+	\begin{definition}
+	  A subset \(K\) of a topological space \(X\) is said to be \textbf{compact} if for every
+	  open cover \(\mathcal U\) of \(K\) (every collection \(\mathcal U\) of open sets
+	  such that \(\bigcup \mathcal U\supseteq K\)) there exists a finite subcollection
+	  \(\mathcal F\subseteq \mathcal U\) that also covers \(K\) (that is,
+	  \(\bigcup\mathcal F\supseteq K\)).
+	\end{definition}
+
+	\begin{theorem}
+	  Any finite union of compact subsets is compact.
 	\end{theorem}
 
+	\begin{proof}
+	$K_1$ and $K_2$ are compact, so let $\mathcal{U}_3$ be an open cover of $K_3 = K_1 \cup K_2$.
+So let $\mathcal{U}_1 = \mathcal{U}_3, \bigcup \mathcal{U}_3 \supseteq K_1$ and $\mathcal{U}_2 = \mathcal{U}_3, \bigcup \mathcal{U}_3 \supseteq K_2$.
+Since $K_1, K_2$ are compact choose finite $\mathcal{F}_1 \subseteq \mathcal{U}_1 = \mathcal{U}_3$ and $\mathcal{F}_2 \subseteq \mathcal{U}_2 = \mathcal{U}_3$, so $\bigcup \mathcal{F}_1 \supseteq K_1$ and $\bigcup \mathcal{F}_2 \supseteq K_2$ and $\bigcup (\mathcal{F}_1 \cup \mathcal{F}_2) \supseteq K_3$.
+Since $\mathcal{F}_1 \cup \mathcal{F}_2$ is a finite subset of $\mathcal{U}_3, K_3$ is compact.
+	\end{proof}
+
+	\begin{proposition}
+	  Any finite subset of a topological space is compact.
+	\end{proposition}
+
+	\begin{proof}
+	For $F = \lbrace x_i : 0 \leq i < n \rbrace \subseteq \mathbb{X}$, let $\mathcal{U}$ be an open covering of $F$ so $\bigcup \mathcal{U} \supseteq F$.
+For each $0 \leq i < n$, let $U_i \in \mathcal{U}$ satisfy $x_i \in U_i$.
+Let finite $\mathcal{F} = \lbrace U_i : 0 \leq i < n \rbrace \subseteq \mathcal{U}$, so $\bigcup \mathcal{F} \supseteq F$ and $F$ is compact.
+	\end{proof}
+
+	\begin{proposition}
+	  The subset \(\{0\}\cup\{\frac{1}{n}:n\in\mathbb Z^+\}\) of \(\mathbb R\) is compact.
+	\end{proposition}
+
+	\begin{proof}
+	Let $K = \lbrace 0 \rbrace \cup \lbrace \frac{1}{n} : n \in \mathbb{Z^+} \rbrace \subseteq \mathbb{R}$ and let $\mathcal{U}$ be an open covering of $K$.
+We may choose $U_0 \in \mathcal{U}$ where $0 \in U_0$.
+So pick $a<b \in \mathbb{R}$ where $0 \in (a, b) \subseteq U_0$.
+Let $N \in \mathbb{Z}^+$ where $0 < \frac{1}{N} < b$.
+Now let finite $F = \lbrace \frac{1}{m} : 1 \leq m < N \rbrace$ so it is compact, and choose $\mathcal{F} \subseteq \mathcal{U}$ with $\bigcup \mathcal{F} \supseteq F$.
+So, $\lbrace \bigcup \mathcal{F} \cup (a,b) \cup U_0 \rbrace \supseteq K$.
+	\end{proof}
+
+	\begin{proposition}
+	  Any unbounded subset of \(\mathbb R\) is not compact.
+	\end{proposition}
+	\begin{proof}
+	Let $K$ be an unbounded subset of $\mathbb{R}$.
+Let $\mathcal{U} = \lbrace (n-2, n) : n \in \mathbb{Z} \rbrace$.
+Let $n_i \in \mathbb{Z}$ be arbitrary for $0 \leq i < n$.
+Then $\mathcal{F} = \lbrace (n_i - 2, n_i) : 0 \leq i < n \rbrace$ is an arbitrary finite sub collection of $\mathcal{U}$.
+However, $\bigcup \mathcal{F} \not\supseteq K$, for $min(n_i-2: 0 \leq i < n)$ and $max(n_i : 0 \leq i < n)$ we can find a $k \in K : k < min(n_i-2: 0 \leq i < n)$ or $k > max(n_i : 0 \leq i < n)$, so $k  \not\in \bigcup \mathcal{F}$ and $K$ is not compact.
+	\end{proof}
+
+	\begin{proposition}
+	  Any open interval \((a,b)\subseteq\mathbb R\) is not compact.
+	\end{proposition}
+	\begin{proof}
+	Let $K = (a, b) \subseteq \mathbb{R}$, Let $\mathcal{U} = \lbrace (x, y) : x, y \in \mathbb{R}, a < x < y < b \rbrace$.
+So, $\bigcup \mathcal{U} \supseteq K$, and $\bigcup \mathcal{U} = K$.
+Let $n \in \mathbb{Z}$, let $x_i, y_i \in \mathbb{R}$ be arbitrary with $0 \leq i < n$.
+Then, $\mathcal{F} = \lbrace (x_i, y_i) : 0 \leq i < n \rbrace$ is an arbitrary finite subset of $\mathcal{U}$.
+However $\bigcup \mathcal{F} \not\supseteq K$, for $min(x_i : 0 \leq i < n)$ we can find a $k \in K : k < min(x_i : 0 \leq i < n)$ which is greater than $a$ so $k \not\in \bigcup \mathcal{F}$ and $K$ is not compact.
+	\end{proof}
+
+	\begin{definition}
+	  A subset \(K\) of a topological space \(X\) is said to be \textbf{Lindel\"of} if for every
+	  open cover \(\mathcal U\) of \(K\) (every collection \(\mathcal U\) of open sets
+	  such that \(\bigcup \mathcal U\supseteq K\)) there exists a countable subcollection
+	  \(\mathcal F\subseteq \mathcal U\) that also covers \(K\) (that is,
+	  \(\bigcup\mathcal F\supseteq K\)).
+	\end{definition}
+
+	\begin{definition}
+	  A subset \(K\) of a topological space \(X\) is said to be \textbf{\(\boldsymbol{\sigma}\)-compact} if
+	  there exist compact subspaces \(K_n\) of \(X\) for \(n\in\mathbb N\) such that
+	  \(K=\bigcup_{n\in\mathbb N} K_n\).
+	  \newline \newline
+	\end{definition}
+	\begin{theorem}
+		Every \(\boldsymbol{\sigma}\)\textbf{-compact} subset of a topological space is \textbf{Lindel\"of}.
+	\end{theorem}
+	\begin{proof}
+	Let $K$ be \(\sigma\)-compact.
+Let $\mathcal{F}_n = \lbrace U_{n0}, U_{n1}, ..., U_{nm} \rbrace$ be a finite subcover of $\mathcal{U}$ for $K_n$.
+So, $\mathcal{C} = \bigcup_{n \in \mathbb{N}} \mathcal{F}_n$ is a countable subcover of $\mathcal{U}$ for $K$.
+Therefore $K$ is Lindel\"of.
+
+	\end{proof}
+
+	\begin{definition}
+	  A subset \(K\) of a topological space \(X\) is said to be \textbf{hemicompact} if there exists compact sets $K_n \subseteq K$ for $n \in \mathbb{N}$ such that for every compact subset \(H\subseteq K\), \(H\subseteq K_n\) for some \(n\in\mathbb N\).
+	\end{definition}
+
+	\begin{theorem}
+		Every \textbf{hemicompact} subset of a topological space is \(\boldsymbol{\sigma}\)\textbf{-compact}.
+	\end{theorem}
+	\begin{proof}
+		Let $K_n \subseteq K$ witness hemicompactness, of course $\underset{n \in \mathbb{N}}{\bigcup}K_n \subseteq K$, since $K_n \subseteq K$.
+Let $k \in K$, so $\lbrace k \rbrace$ is compact and $\bigcup\lbrace k \rbrace = K$.
+For $k_n \in K$, choose $K_n : k_n \in K_n \subseteq K$, so $K = \underset{n \in \mathbb{N}}{\bigcup}K_n$
+	\end{proof}
+
+	\begin{definition}
+		$X$ is \textbf{locally compact} if for every $x \in X$ there exists an open set $U$ and compact $K$ with $x \in U \subseteq K$.
+	\end{definition}
+
+	\begin{definition}
+		$x$ is a \textbf{cluster point} of $\langle p_n \rangle_{n < \omega}$ if and only if for every neighborhood $U$ of $x$, $U$ hits infinitely many $p_n$.
+	\end{definition}
+
+\section{Topological Games}
+
+	\begin{definition}
+		$\boldsymbol{Gru_{\mathcal{K},\mathcal{P}}(X)}$ is a game defined as the $Gruenhage compact/point game$ with players $\mathcal{K}$, $mathcal{P}$ played on a topological space $X$.
+During round $n$, $\mathcal{K}$ chooses a compact subset $K_n$ of $X$, followed by $\mathcal{P}$ choosing a point $p_n \in X$ such that $p_n \not\in \bigcup_{m\leq n}K_m$.
+$\mathcal{K}$ wins if and only if $\langle p_n \rangle_{n<\omega}$ lacks a \textbf{cluster point}.
+	\end{definition}
+
+	\begin{definition}
+	$\boldsymbol{\mathcal{K} \underset{pre}{\uparrow} Gru_{\mathcal{K}, \mathcal{P}}(X)}$ is the statement that $\mathcal{K}$ has a winning strategy $\sigma : \omega \rightarrow \mathcal{K}(X)$ that depends only on the round number (ignores the moves of $\mathcal{P}$).
+	\end{definition}
+
+	\begin{theorem}
+		If $X$ is \textbf{Lindel\"of} and locally compact, then $\boldsymbol{\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)}$
+	\end{theorem}
+	\begin{proof}
+		For $x \in X$, let $x \in U_x \subseteq K_x$ for $U_x$ open and $K_x$ compact.
+Then by definition of Lindel\"of choose $U_n \in \mathcal{U} = \lbrace U_x : x \in X \rbrace$ such that $\underset{n \in \mathbb{N}}{\bigcup}U_n = X$.
+Then for each $U_n$, there exists compact $K_n$ where $U_n \subseteq K_n$.
+\newline
+		For $Gru_{\mathcal{K}, \mathcal{P}} (X)$, let $\sigma(n) = K_n$ denote a strategy for $\mathcal{K}$, $\mathcal{K}$ chooses compact $K_n \supseteq U_n \in \mathcal{C}$ and $\mathcal{P}$ chooses $p \in X$ such that $p \not\in K_n$.
+$\lbrace K_i : i < \omega \rbrace$ is countable and $\bigcup \lbrace K_i : i < \omega \rbrace \supseteq X$.
+For $\mathcal{P}$ to win, there must be $U_n \in \mathcal{C}$ such that $\sigma(n) \not\supseteq U_n$, but we've already established that $\bigcup \lbrace K_i : i < \omega \rbrace \supseteq X$ so contradiction, thus $\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)$.
+	\end{proof}
+
+	\begin{lemma}
+	Let $K$ be a compact subset of $X$. If $\langle p_n \rangle$ is a sequence of points in $K$, then $\langle p_n \rangle$ has a cluster point.
+	\end{lemma}
+	\begin{proof}
+	This is obviously true if the sequence only uses finitely many different points (one point must be repeated infinitely often, so it is its own cluster point).
+So without loss of generality $\langle p_n \rangle$ uses infinitely many different points.
+If $\langle p_n \rangle$ didn't have a cluster point, then for each $x \in K$, let $U_x$ contain only finitely many $p_n$.
+$\lbrace U_x : x \in K \rbrace$ covers $K$, so choose $x_i$ for $i \leq n : \lbrace U_{x_i} : i \leq n \rbrace$ covers $K$.
+But each $U_{x_i}$ contains only finitely many $p_n$, so $\langle p_n \rangle$ cannot have infinitely many different points to choose, contradiction.
+So $\langle p_n \rangle$ does have a cluster point.
+	\end{proof}
+
+	\begin{theorem}
+		$\boldsymbol{\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)} \Rightarrow X$ is \textbf{hemicompact}.
+	\end{theorem}
+	\begin{proof}
+		We prove the contrapositive.
+Let $\sigma$ be a predetermined strategy, and assume $X$ isn't hemicompact.
+So there exists a compact $K$ that isn't a union of finite $\sigma(n)$, so player $\mathcal{P}$ may always legally choose a point $p_n \in K$.
+Then by the lemma, $\langle p_n \rangle$ has a cluster point.
+Therefore $\sigma$ isn't a winning strategy.
+	\end{proof}
 \end{document}

### 2018-05-02 project.tex
Update - Article

@@
 	\begin{definition}
-	  A subset \(K\) of a topological space \(X\) is said to be \textbf{hemicompact} if
-	  for every compact subset \(H\subseteq K\),
-	  \(H\subseteq K_n\) for some \(n\in\mathbb N\).
+	  A subset \(K\) of a topological space \(X\) is said to be \textbf{hemicompact} if there exists compact sets $K_n \subseteq K$ for $n \in \mathbb{N}$ such that for every compact subset \(H\subseteq K\), \(H\subseteq K_n\) for some \(n\in\mathbb N\).
 	\end{definition}
@@
 	\begin{proof}
-		For all compact $C \subseteq K \subseteq X$, $C \subseteq K_{n \in \mathbb{N}} \subseteq K$. \newline
-		$K_{n \in \mathbb{N}} \subseteq X$.
-Since all compact $C_{i \in \mathbb{N}}$ are subsets of some $K_{n \in \mathbb{N}}$, $\underset{n \in \mathbb{N}}{\bigcup}K_n \supseteq \underset{i \in \mathbb{N}}{\bigcup} C_i$ so $\underset{n\in\mathbb{N}}{\bigcup}K_n = K$.
+		Let $K_n \subseteq K$ witness hemicompactness, of course $\underset{n \in \mathbb{N}}{\bigcup}K_n \subseteq K$, since $K_n \subseteq K$.
+Let $k \in K$, so $\lbrace k \rbrace$ is compact and $\bigcup\lbrace k \rbrace = K$.
+For $k_n \in K$, choose $K_n : k_n \in K_n \subseteq K$, so $K = \underset{n \in \mathbb{N}}{\bigcup}K_n$
 	\end{proof}
@@
 	\begin{definition}
-		$\boldsymbol{Gru_{\mathcal{K},\mathcal{P}}(X)}$ is a game defined as... $\mathcal{K}$ wins if and only if $\langle p_n \rangle_{n<\omega}$ lacks a \textbf{cluster point}. 
+		$\boldsymbol{Gru_{\mathcal{K},\mathcal{P}}(X)}$ is a game defined as the $Gruenhage compact/point game$ with players $\mathcal{K}$, $mathcal{P}$ played on a topological space $X$.
+During round $n$, $\mathcal{K}$ chooses a compact subset $K_n$ of $X$, followed by $\mathcal{P}$ choosing a point $p_n \in X$ such that $p_n \not\in \bigcup_{m\leq n}K_m$.
+$\mathcal{K}$ wins if and only if $\langle p_n \rangle_{n<\omega}$ lacks a \textbf{cluster point}.
 	\end{definition}
@@
 	\begin{theorem}
-		If $X$ is \textbf{Lindel\"of}, then $\boldsymbol{\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)}$
+		If $X$ is \textbf{Lindel\"of} and locally compact, then $\boldsymbol{\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)}$
 	\end{theorem}
 	\begin{proof}
-		Let $X$ be Lindel\"of, so there is a countable subcollection $\mathcal{C} \subseteq \mathcal{U}$, where $\mathcal{U}$ is an arbitrary covering of $X$.
-So, $\mathcal{C} = \lbrace U_n : U_n \in \mathcal{U}, n < \omega \rbrace$ and $\bigcup \mathcal{C} \supseteq X$.\newline \newline
-		For $Gru_{\mathcal{K}, \mathcal{P}}(X)$, $\mathcal{K}$ chooses compact $K_{i \leq n < \omega} \supseteq U_{n < \omega} \in \mathcal{C}$ and $\mathcal{P}$ chooses $p \in X$ such that $p \not\in K_{i \leq n < \omega}$.
-Since $\lbrace K_i : i \leq n < \omega \rbrace$ is countable and $\bigcup \lbrace K_i : i \leq n < \omega \rbrace \supseteq X$, $\mathcal{P}$ has countably many $p_{m \leq n < \omega}$.
-Therefore $\langle p_m \rangle$ is finite and $X$ has no cluster points.
-Thus, $\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)$.
+		For $x \in X$, let $x \in U_x \subseteq K_x$ for $U_x$ open and $K_x$ compact.
+Then by definition of Lindel\"of choose $U_n \in \mathcal{U} = \lbrace U_x : x \in X \rbrace$ such that $\underset{n \in \mathbb{N}}{\bigcup}U_n = X$.
+Then for each $U_n$, there exists compact $K_n$ where $U_n \subseteq K_n$.
+\newline
+		For $Gru_{\mathcal{K}, \mathcal{P}} (X)$, let $\sigma(n) = K_n$ denote a strategy for $\mathcal{K}$, $\mathcal{K}$ chooses compact $K_n \supseteq U_n \in \mathcal{C}$ and $\mathcal{P}$ chooses $p \in X$ such that $p \not\in K_n$.
+$\lbrace K_i : i < \omega \rbrace$ is countable and $\bigcup \lbrace K_i : i < \omega \rbrace \supseteq X$.
+For $\mathcal{P}$ to win, there must be $U_n \in \mathcal{C}$ such that $\sigma(n) \not\supseteq U_n$, but we've already established that $\bigcup \lbrace K_i : i < \omega \rbrace \supseteq X$ so contradiction, thus $\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)$.
 	\end{proof}
@@
 	This is obviously true if the sequence only uses finitely many different points (one point must be repeated infinitely often, so it is its own cluster point).
-So assume $\langle p_n \rangle$ uses infinitely many different points.
+So without loss of generality $\langle p_n \rangle$ uses infinitely many different points.
 If $\langle p_n \rangle$ didn't have a cluster point, then for each $x \in K$, let $U_x$ contain only finitely many $p_n$.
 $\lbrace U_x : x \in K \rbrace$ covers $K$, so choose $x_i$ for $i \leq n : \lbrace U_{x_i} : i \leq n \rbrace$ covers $K$.
-But each $U_{x_i}$ contains only finitely many $p_n$, so $\langle p_n \rangle$ cannot have infinitely many different points to choose from and $\langle p_n \rangle$ does not have a cluster point.
+But each $U_{x_i}$ contains only finitely many $p_n$, so $\langle p_n \rangle$ cannot have infinitely many different points to choose, contradiction.
+So $\langle p_n \rangle$ does have a cluster point.
 	\end{proof}

### 2018-05-03 article.tex
Corrections and Bibliography

@@
 
-	\begin{theorem}
+	\begin{proposition}
 		The ``topology generated by \(\mathcal{B}\)'' is actually a topology.
-	\end{theorem}
-	\begin{proof} 
-	This was not finished correctly and fell through the cracks of time. Should it be removed?
-	\end{proof}
+	\end{proposition}
 
@@
 
-	\begin{theorem}
+	\begin{proposition}
 	$\lbrace($a, b$)$ : a $<$ b $\in \mathbb{Q}\rbrace$ is a basis for the Euclidean topology.
-	\end{theorem}
-	\begin{proof}:\newline
-		\begin{enumerate}
-		\item Let $\mathcal{B} = \lbrace (a, b) : a < b \in \mathbb{Q}\rbrace$ Let $x \in \mathbb{R}$ then, $\lfloor x \rfloor -1 < x < \lceil x \rceil + 1$.
-Let B = $(\lfloor x \rfloor -1, \lceil x \rceil + 1)$, so $x \in B \in \mathcal{B}$ and $B \subseteq \mathbb{Q}$.
-		\item Now, for $B_1, B_2 \in \mathcal{B}, \exists x \in B_1 \cap B_2 : x \in B_1$ and $x \in B_2$.
-$a_1, a_2 < b_1, b_2 \in \mathbb{Q}.$ Let $B_1 = (a_1, b_1)$ and $B_2 = (a_2, b_2)$.
-Now let $B_3 = (max(a_1,a_2), min(b_1,b_2))$ with $a_1,a_2<x<b_1,b_2$ so $x \in B_3$.
-So, $x \in B_3 \subseteq B_1 \cap B_2$.
-		\item Now show it generates $\tau$...
-		\end{enumerate} 
-	\end{proof}
+	\end{proposition}
 
-\section{Compactness Properties}
+\section{Covering Properties}
 
@@
 		Let $K_n \subseteq K$ witness hemicompactness, of course $\underset{n \in \mathbb{N}}{\bigcup}K_n \subseteq K$, since $K_n \subseteq K$.
-Let $k \in K$, so $\lbrace k \rbrace$ is compact and $\bigcup\lbrace k \rbrace = K$.
-For $k_n \in K$, choose $K_n : k_n \in K_n \subseteq K$, so $K = \underset{n \in \mathbb{N}}{\bigcup}K_n$
+Let $k \in K$, so $\lbrace k \rbrace$ it compact, thus there is some $n \in \mathbb{N}$ such that $\lbrace k \rbrace \subseteq K_n$.
+Therefore $k \in K_n \subseteq K$, so $K = \underset{n \in \mathbb{N}}{\bigcup}K_n$.
 	\end{proof}
@@
 	\end{definition}
+
+	\begin{lemma}
+	Let $K$ be a compact subset of $X$. If $\langle p_n \rangle$ is a sequence of points in $K$, then $\langle p_n \rangle$ has a cluster point.
+	\end{lemma}
+	\begin{proof}
+	This is obviously true if the sequence only uses finitely many different points (one point must be repeated infinitely often, so it is its own cluster point).
+So without loss of generality $\langle p_n \rangle$ uses infinitely many different points.
+If $\langle p_n \rangle$ didn't have a cluster point, then for each $x \in K$, let $U_x$ contain only finitely many $p_n$.
+$\lbrace U_x : x \in K \rbrace$ covers $K$, so choose $x_i$ for $i \leq n : \lbrace U_{x_i} : i \leq n \rbrace$ covers $K$.
+But each $U_{x_i}$ contains only finitely many $p_n$, so $\langle p_n \rangle$ cannot have infinitely many different points to choose, contradiction.
+So $\langle p_n \rangle$ does have a cluster point.
+	\end{proof}
 
@@
 \newline
-		For $Gru_{\mathcal{K}, \mathcal{P}} (X)$, let $\sigma(n) = K_n$ denote a strategy for $\mathcal{K}$, $\mathcal{K}$ chooses compact $K_n \supseteq U_n \in \mathcal{C}$ and $\mathcal{P}$ chooses $p \in X$ such that $p \not\in K_n$.
+		For $Gru_{\mathcal{K}, \mathcal{P}} (X)$, let $\sigma(n) = K_n$ denote a strategy for $\mathcal{K}$, $\mathcal{K}$ chooses compact $K_n \supseteq U_n \in \mathcal{C}$ and $\mathcal{P}$ chooses $p \in X$ such that $p \not\in \underset{m \leq n}{\bigcup}K_m$.
 $\lbrace K_i : i < \omega \rbrace$ is countable and $\bigcup \lbrace K_i : i < \omega \rbrace \supseteq X$.
-For $\mathcal{P}$ to win, there must be $U_n \in \mathcal{C}$ such that $\sigma(n) \not\supseteq U_n$, but we've already established that $\bigcup \lbrace K_i : i < \omega \rbrace \supseteq X$ so contradiction, thus $\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)$.
-	\end{proof}
-
-	\begin{lemma}
-	Let $K$ be a compact subset of $X$. If $\langle p_n \rangle$ is a sequence of points in $K$, then $\langle p_n \rangle$ has a cluster point.
-	\end{lemma}
-	\begin{proof}
-	This is obviously true if the sequence only uses finitely many different points (one point must be repeated infinitely often, so it is its own cluster point).
-So without loss of generality $\langle p_n \rangle$ uses infinitely many different points.
-If $\langle p_n \rangle$ didn't have a cluster point, then for each $x \in K$, let $U_x$ contain only finitely many $p_n$.
-$\lbrace U_x : x \in K \rbrace$ covers $K$, so choose $x_i$ for $i \leq n : \lbrace U_{x_i} : i \leq n \rbrace$ covers $K$.
-But each $U_{x_i}$ contains only finitely many $p_n$, so $\langle p_n \rangle$ cannot have infinitely many different points to choose, contradiction.
-So $\langle p_n \rangle$ does have a cluster point.
+For $\mathcal{P}$ to win, there must be an $x \in X$ such that for every neighborhood $U$ of $x$, $U$ hits infinitely many $p_n$, but$x \in U_m \subseteq K_m$ for some $n < \omega$ and $p_n \not\in K_m$ for $n \geq m$.
+So there is no such $x$ and $\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)$.
 	\end{proof}
@@
 So there exists a compact $K$ that isn't a union of finite $\sigma(n)$, so player $\mathcal{P}$ may always legally choose a point $p_n \in K$.
-Then by the lemma, $\langle p_n \rangle$ has a cluster point.
+Then by the lemma, $\langle p_n \rangle$ has a cluster point because for each $x \in K$ there is a $U_x$ that contains infinitely many $p_n$, and $\lbrace U_x : x \in K \rbrace$ covers $K$.
 Therefore $\sigma$ isn't a winning strategy.
 	\end{proof}
+
+\bibliographystyle{plain}
+\bibliography{bib}
+
 \end{document}
